### 2015-11-14 manuscript.tex
First commit!

\documentclass{article}
% \usepackage[margin=2.5cm]{geometry}
\usepackage[margin=2.5cm, headheight=0pt, headsep=1cm]{geometry}
\usepackage{enumerate, fancyhdr, graphicx, amsmath, nth}
\usepackage[binary-units=true]{siunitx}

\title{Exit Strategy}
\author{Paul Chesnais, Antoine Pourchet and Ryan Vogan}
\date{\today}

\pagestyle{fancy}
\fancyhead{}
\lhead{Chesnais, Pourchet, Vogan}
\chead{Exit Strategy}
\rhead{\today}
\fancyfoot{}
\rfoot{\thepage}
\lfoot{\includegraphics[height=20pt]{http://paul.chesnais.com/assets/favicon.png}}
\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0.5pt}

\usepackage{listings, color, times, textcomp, float, hyperref, setspace, subcaption}
\definecolor{Code}{rgb}{0,0,0}
\definecolor{Decorators}{rgb}{0.5,0.5,0.5}
\definecolor{Numbers}{rgb}{0.5,0,0}
\definecolor{MatchingBrackets}{rgb}{0.25,0.5,0.5}
\definecolor{Keywords}{rgb}{0,0,1}
\definecolor{self}{rgb}{0,0,0}
\definecolor{Strings}{rgb}{0,0.63,0}
\definecolor{Comments}{rgb}{0,0.63,1}
\definecolor{Backquotes}{rgb}{0,0,0}
\definecolor{Classname}{rgb}{0,0,0}
\definecolor{FunctionName}{rgb}{0,0,0}
\definecolor{Operators}{rgb}{0,0,0}
\definecolor{Background}{rgb}{0.98,0.98,0.98}

\lstset{numbers=left,numberstyle=\footnotesize,numbersep=1em,xleftmargin=1em,
framextopmargin=2em,framexbottommargin=2em,showspaces=false,showtabs=false,
showstringspaces=false,frame=l,tabsize=4,basicstyle=\ttfamily\small\setstretch{1},
backgroundcolor=\color{Background},language=Python,
commentstyle=\color{Comments}\slshape,stringstyle=\color{Strings},
morecomment=[s][\color{Strings}]{"""}{"""},
morecomment=[s][\color{Strings}]{'''}{'''},morekeywords={import,from,class,def,
for,while,if,is,in,elif,else,not,and,or,print,break,continue,return,True,False,
None,access,as,del,except,exec,finally,global,import,lambda,pass,print,raise,try,
assert},keywordstyle={\color{Keywords}\bfseries},morekeywords={[2]@invariant},
keywordstyle={[2]\color{Decorators}\slshape},emph={self},
emphstyle={\color{self}\slshape},breaklines=true}

\begin{document}
\maketitle
\thispagestyle{empty}

\href{http://paul.chesnais.com/assets/favicon.png}{blop}

\begin{thebibliography}{9}
  \bibitem{pmc}
    \url{http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4060166/}
\end{thebibliography}

\end{document}

### 2015-11-14 maketex.py

@@ -1,0 +1,200 @@
+#!/usr/bin/python
+
+import sys
+import os
+import argparse
+from subprocess import Popen
+
+DEVNULL = open(os.devnull, 'wb')
+
+gitignore = """\
+%s.*
+!%s
+.build/"""
+
+classes = {'3': 'MATH 3610',  '4': 'CS 4320',  'A': 'ASTRO 3310',  'C': 'CS 4700',  'E': 'ECON 1110',  'P': 'PRAC CS 4700'}
+
+extras = {
+    '3': r"""\usepackage{float}
+\usepackage{listings, color, times, textcomp, float}
+\definecolor{mygreen}{RGB}{28,172,0} % color values Red, Green, Blue
+\definecolor{mylilas}{RGB}{170,55,241}
+\lstset{language=Matlab, basicstyle=\scriptsize\ttfamily,breaklines=true,
+frame=single,morekeywords={matlab2tikz},keywordstyle=\color{blue},
+morekeywords=[2]{1},keywordstyle=[2]{\color{black}},
+identifierstyle=\color{black},stringstyle=\color{mylilas},
+commentstyle=\color{mygreen},showstringspaces=false, numbers=left,
+numberstyle={\tiny \color{black}},numbersep=9pt,emph=[1]{for,end,break},
+emphstyle=[1]\color{red},literate={~} {\texttildelow}{1}}""",
+    '4': r"""\usepackage{listings, times}
+\usepackage[usenames,dvipsnames]{xcolor}
+\lstset{language=SQL,basicstyle=\ttfamily\small,numbers=left,
+numberstyle=\footnotesize,stepnumber=0,numbersep=5pt,
+backgroundcolor=\color{white},commentstyle=\color{Aquamarine},
+keywordstyle=\color{OrangeRed},showspaces=false,showstringspaces=false,
+showtabs=false,frame=single,tabsize=2,captionpos=b,
+breaklines=true,breakatwhitespace=false,moredelim=**[is][\color{black}]{@}{@}}""",
+    'A': r'\usepackage[binary-units=true]{siunitx}',
+    'E': '',
+    'C': r"""\usepackage{tikz, caption,subcaption, float}
+\usetikzlibrary{arrows}
+\usetikzlibrary{positioning}""",
+    'P': ''
+}
+
+makefile_extras = {
+    '3': '',
+    '4': '',
+    'A': '',
+    'E': '',
+    'C': '',
+    'P': ''
+}
+
[…]

### 2015-11-14 maketex.py
Whoops, included something

@@ -1,200 +1,0 @@
-#!/usr/bin/python
-
-import sys
-import os
-import argparse
-from subprocess import Popen
-
-DEVNULL = open(os.devnull, 'wb')
-
-gitignore = """\
-%s.*
-!%s
-.build/"""
-
-classes = {'3': 'MATH 3610',  '4': 'CS 4320',  'A': 'ASTRO 3310',  'C': 'CS 4700',  'E': 'ECON 1110',  'P': 'PRAC CS 4700'}
-
-extras = {
-    '3': r"""\usepackage{float}
-\usepackage{listings, color, times, textcomp, float}
-\definecolor{mygreen}{RGB}{28,172,0} % color values Red, Green, Blue
-\definecolor{mylilas}{RGB}{170,55,241}
-\lstset{language=Matlab, basicstyle=\scriptsize\ttfamily,breaklines=true,
-frame=single,morekeywords={matlab2tikz},keywordstyle=\color{blue},
-morekeywords=[2]{1},keywordstyle=[2]{\color{black}},
-identifierstyle=\color{black},stringstyle=\color{mylilas},
-commentstyle=\color{mygreen},showstringspaces=false, numbers=left,
-numberstyle={\tiny \color{black}},numbersep=9pt,emph=[1]{for,end,break},
-emphstyle=[1]\color{red},literate={~} {\texttildelow}{1}}""",
-    '4': r"""\usepackage{listings, times}
-\usepackage[usenames,dvipsnames]{xcolor}
-\lstset{language=SQL,basicstyle=\ttfamily\small,numbers=left,
-numberstyle=\footnotesize,stepnumber=0,numbersep=5pt,
-backgroundcolor=\color{white},commentstyle=\color{Aquamarine},
-keywordstyle=\color{OrangeRed},showspaces=false,showstringspaces=false,
-showtabs=false,frame=single,tabsize=2,captionpos=b,
-breaklines=true,breakatwhitespace=false,moredelim=**[is][\color{black}]{@}{@}}""",
-    'A': r'\usepackage[binary-units=true]{siunitx}',
-    'E': '',
-    'C': r"""\usepackage{tikz, caption,subcaption, float}
-\usetikzlibrary{arrows}
-\usetikzlibrary{positioning}""",
-    'P': ''
-}
-
-makefile_extras = {
-    '3': '',
-    '4': '',
-    'A': '',
-    'E': '',
-    'C': '',
-    'P': ''
-}
-
[…]

### 2015-11-14 manuscript.tex
Added lstlistings stuff

@@
 \rfoot{\thepage}
-\lfoot{\includegraphics[height=20pt]{http://paul.chesnais.com/assets/favicon.png}}
+\lfoot{\includegraphics[height=20pt]{Logo}}
 \renewcommand{\headrulewidth}{0.5pt}
@@
 \definecolor{Background}{rgb}{0.98,0.98,0.98}
+\definecolor{mygreen}{RGB}{28,172,0}
+\definecolor{mylilas}{RGB}{170,55,241}
 
-\lstset{numbers=left,numberstyle=\footnotesize,numbersep=1em,xleftmargin=1em,
-framextopmargin=2em,framexbottommargin=2em,showspaces=false,showtabs=false,
-showstringspaces=false,frame=l,tabsize=4,basicstyle=\ttfamily\small\setstretch{1},
-backgroundcolor=\color{Background},language=Python,
-commentstyle=\color{Comments}\slshape,stringstyle=\color{Strings},
-morecomment=[s][\color{Strings}]{"""}{"""},
-morecomment=[s][\color{Strings}]{'''}{'''},morekeywords={import,from,class,def,
-for,while,if,is,in,elif,else,not,and,or,print,break,continue,return,True,False,
-None,access,as,del,except,exec,finally,global,import,lambda,pass,print,raise,try,
-assert},keywordstyle={\color{Keywords}\bfseries},morekeywords={[2]@invariant},
-keywordstyle={[2]\color{Decorators}\slshape},emph={self},
-emphstyle={\color{self}\slshape},breaklines=true}
+\lstdefinestyle{python}{
+  backgroundcolor=\color{Background},basicstyle=\ttfamily\small\setstretch{1},breaklines=true,
+  commentstyle=\color{Comments}\slshape,emph={self},emphstyle={\color{self}\slshape},frame=l,framexbottommargin=2em,
+  framextopmargin=2em,keywordstyle={[2]\color{Decorators}\slshape},keywordstyle={\color{Keywords}\bfseries},
+  language=Python,morecomment=[s][\color{Strings}]{"""}{"""},morecomment=[s][\color{Strings}]{'''}{'''},
+  morekeywords={[2]@invariant},morekeywords={import,from,class,def,for,while,if,is,in,elif,else,not,and,or,print,break,
+  continue,return,True,False,None,access,as,del,except,exec,finally,global,import,lambda,pass,print,raise,try,assert},
+  numbers=left,numbersep=1em,numberstyle=\footnotesize,showspaces=false,showstringspaces=false,showtabs=false,
+  stringstyle=\color{Strings},tabsize=4,xleftmargin=1em,
+}
+
+\lstdefinestyle{matlab}{
+  backgroundcolor=\color{Background},basicstyle=\ttfamily\small\setstretch{1},breaklines=true,
+  commentstyle=\color{mygreen},emph=[1]{for,end,break},emphstyle=[1]\color{red},frame=l,identifierstyle=\color{black},
+  keywordstyle=[2]{\color{black}},keywordstyle=\color{blue},language=Matlab,literate={~} {\texttildelow}{1},
+  morekeywords=[2]{1},morekeywords={matlab2tikz},numbers=left,numbersep=9pt,numberstyle={\tiny \color{black}},
+  showstringspaces=false,stringstyle=\color{mylilas},
+}
 
@@
 
-\href{http://paul.chesnais.com/assets/favicon.png}{blop}
+\section{Abstract}
+\label{sec:abstract}
+
+\section{Executive Summary}
+\label{sec:executive_summary}
+
+% Antoine's stuff and thing
+\section{Deterministic Model}
+\label{sec:deterministic_model}
+
+% Paul's stuff and things
+\section{Stochastic Model}
+\label{sec:stochastic_model}
+
+\begin{lstlisting}[style=python]
+class Bloop:
+  def __init__(self):
+    yourmother
+\end{lstlisting}
 

### 2015-11-14 manuscript.tex
Quite

--- 2015-11-14 manuscript.tex
@@
 \definecolor{Background}{rgb}{0.98,0.98,0.98}
+\definecolor{mygreen}{RGB}{28,172,0}
+\definecolor{mylilas}{RGB}{170,55,241}
 
-\lstset{numbers=left,numberstyle=\footnotesize,numbersep=1em,xleftmargin=1em,
-framextopmargin=2em,framexbottommargin=2em,showspaces=false,showtabs=false,
-showstringspaces=false,frame=l,tabsize=4,basicstyle=\ttfamily\small\setstretch{1},
-backgroundcolor=\color{Background},language=Python,
-commentstyle=\color{Comments}\slshape,stringstyle=\color{Strings},
-morecomment=[s][\color{Strings}]{"""}{"""},
-morecomment=[s][\color{Strings}]{'''}{'''},morekeywords={import,from,class,def,
-for,while,if,is,in,elif,else,not,and,or,print,break,continue,return,True,False,
-None,access,as,del,except,exec,finally,global,import,lambda,pass,print,raise,try,
-assert},keywordstyle={\color{Keywords}\bfseries},morekeywords={[2]@invariant},
-keywordstyle={[2]\color{Decorators}\slshape},emph={self},
-emphstyle={\color{self}\slshape},breaklines=true}
+\lstdefinestyle{Python}{
+  backgroundcolor=\color{Background},basicstyle=\ttfamily\small\setstretch{1},breaklines=true,
+  commentstyle=\color{Comments}\slshape,emph={self},emphstyle={\color{self}\slshape},frame=l,framexbottommargin=2em,
+  framextopmargin=2em,keywordstyle={[2]\color{Decorators}\slshape},keywordstyle={\color{Keywords}\bfseries},
+  language=Python,morecomment=[s][\color{Strings}]{"""}{"""},morecomment=[s][\color{Strings}]{'''}{'''},
+  morekeywords={[2]@invariant},morekeywords={import,from,class,def,for,while,if,is,in,elif,else,not,and,or,print,break,
+  continue,return,True,False,None,access,as,del,except,exec,finally,global,import,lambda,pass,print,raise,try,assert},
+  numbers=left,numbersep=1em,numberstyle=\footnotesize,showspaces=false,showstringspaces=false,showtabs=false,
+  stringstyle=\color{Strings},tabsize=4,xleftmargin=1em,
+}
+
+\lstdefinestyle{Matlab}{
+  backgroundcolor=\color{Background},basicstyle=\ttfamily\small\setstretch{1},breaklines=true,
+  commentstyle=\color{mygreen},emph=[1]{for,end,break},emphstyle=[1]\color{red},frame=l,identifierstyle=\color{black},
+  keywordstyle=[2]{\color{black}},keywordstyle=\color{blue},language=Matlab,literate={~} {\texttildelow}{1},
+  morekeywords=[2]{1},morekeywords={matlab2tikz},numbers=left,numbersep=9pt,numberstyle={\tiny \color{black}},
+  showstringspaces=false,stringstyle=\color{mylilas},
+}
 
@@
 
-\href{http://paul.chesnais.com/assets/favicon.png}{blop}
+\section{Abstract}
+\label{sec:abstract}
+
+\section{Executive Summary}
+\label{sec:executive_summary}
+
+% Antoine's stuff and thing
+\section{Deterministic Model}
+\label{sec:deterministic_model}
+
+% Paul's stuff and things
+\section{Stochastic Model}
+\label{sec:stochastic_model}
 

### 2015-11-14 get_adjacency.py
Added lake code

@@ -1,0 +1,51 @@
+#! /usr/bin/python
+
+import csv
+
+def get_name_map(filename):
+    with open(filename, 'rb') as fh:
+        h = {}
+        counter = 0
+        for line in fh:
+            h[line.strip()] = counter
+            counter += 1
+
+        return h
+
+def get_pairs(filename, names):
+    with open(filename, 'rb') as csvfile:
+        pairs = []
+        r = csv.reader(csvfile)
+        for row in r:
+            a = names[row[0]]
+            b = names[row[1]]
+            t = (a, b, row[2])
+            pairs.append(t)
+
+        return pairs
+
+def get_adjacency(pairs):
+    matsize = max(pairs, key=maxpair)
+    mat = [[0 for a in range(matsize)] for a in range(matsize)]
+    for p in pairs:
+        mat[p[1]][p[0]] = p[2]
+
+    return mat
+
+def maxpair(p):
+    return max(p[:2])
+
+def to_matlab(mat):
+    s = '['
+    for row in mat:
+        s += str(row) + ';'
+
+    return s + ']'
+
+if __name__ == "__main__":
+    names = get_name_map("mississippi_county.list")
+    pairs = get_pairs("graph.csv", names)
+    mat = get_adjacency(pairs)
+    s = to_matlab(mat)
+    print s
+

### 2015-11-14 lakes/lakes.m

@@ -1,0 +1,65 @@
+% The chemical dissolving in interconnected "lakes" problem.
+% Our basic assumption is that the volume of each "lake" 
+% stays constant.  Can you re-write the system of ODEs for the more general
+% case?
+
+%This script deals with 3 reservoirs only 
+%-- see the other 2 files for the general case.
+
+n = 3; %the number of lakes
+
+% The volumes of lakes in km^3
+V = ones(1,n);
+
+% The mutal flow rates matrix
+% r(i,j) = # of (km^3) of water passing from lake j to lake i per day.
+%
+% Note: all entries are non-negative (the direction of flow is specified).
+% A zero entry means no channel.  If both r(i,j) and r(j,i) are non-zero,
+% this means that there are two separate uni-directional channels: 
+% from i to j and from j to i.
+
+
+% The fully connected equally weighted graph of channels.
+r = 1e-2 * [
+    0   1   1
+    1   0   1
+    1   1   0];
+
+% The loop of channels.
+% Lake1 feeds into Lake2, which feeds into Lake3, which feeds into Lake1.
+% 
+% r = 1e-2 * [
+%     0   0   1
+%     1   0   0
+%     0   1   0];
+
+R = sum(r);
+
+%Build the ODE matrix  
+%(note: there are more efficient ways to do this, but this one is simple & readable)
+A = r;
+for i=1:n
+    A(i,i) = - R(i);
+    A(i,:) = A(i,:) / V(i);
+end
+
+t_star = 400;  %after how many days will we check the concentrations?
+
+c0 = [1;0;0];
+
+
+%The ODE system is c'(t) = A c(t)
+
+cc=[];  %the history of concentrations
+for t=0:t_star
+    B = expm(t*A);
+    c = B * c0;
+    cc= [cc c];
+end
+
+close all;
+plot(cc');  
+legend('Lake 1', 'Lake 2', 'Lake 3');
+xlabel('t');
+ylabel('c');

### 2015-11-14 lakes/lakes1.m

@@ -1,0 +1,74 @@
+% The chemical dissolving in interconnected "lakes" problem.
+%
+% Our basic assumption is that the volume of each "lake" 
+% stays constant.  Can you re-write the system of ODEs to
+% handle the more general case?
+
+
+%initial concentrations of chemicals in each lake
+c0 = [1;0;1;0;0;0];
+%c0 = [3;0;0;0;1;0];
+%c0 = [2;0;0;0;1;0];
+
+
+n = length(c0); %the number of lakes
+
+% The volumes of lakes in km^3
+V = ones(1,n+1);
+V(n+1) = 1e8;
+
+% The mutal flow rates matrix
+% r(i,j) = # of (km^3) of water passing from lake j to lake i per day.
+%
+% Note: all entries are non-negative (the direction of flow is specified).
+% A zero entry means no channel.  If both r(i,j) and r(j,i) are non-zero,
+% this means that there are two separate uni-directional channels: 
+% from i to j and from j to i.
+
+% The loop of channels. 
+% Lake 1 feeds into Lake 2, which feeds into Lake 3, etc...
+r = diag(ones(1,n-1),-1);
+r(1,n) = 1;
+r = 1e-2 * r;
+r = [r zeros(6,1); zeros(1,7)];
+r(n+1,1) = 0.005;
+r(1,n+1) = 0.005;
+
+R = sum(r);
+
+%Build the ODE matrix  
+%(note: there are more efficient ways to do this, but this one is simple & readable)
+A = r;
+for i=1:n+1
+    A(i,i) = - R(i);
+    A(i,:) = A(i,:) / V(i);
+end
+
+t_star = 1000;  %after how many days will we check the concentrations?
+
+
+%The ODE system is c'(t) = A c(t)
+
+cc=[];  %the history of concentrations
+opttime = 0;
+for t=0:t_star
+    B = expm(t*A);
+    c = B * [c0; 0];
+    %Note: for every i, the i-th column of B can be interpreted as c(t) 
+    %corresponding to a very special initial condition: 
+    %concentration 1 in the i-th lake & concentration 0 everywhere else.
+    %In fact, c=B*c0 is the "linear superposition principle" at work!
+    
+    cc= [cc c];
+    m = max(c(1:n));
+    if m <= 0.2 && opttime == 0
+        opttime = t;
+    end
+end
+
+close all;
+hold on;
+plot(cc');
[…]

### 2015-11-14 lakes/lakes2.m

@@ -1,0 +1,53 @@
+function lakes_test
+c0 = [1;0;1;0;0;0];
+%c0 = [3;0;0;0;1;0];
+%c0 = [2;0;0;0;1;0];
+
+n = length(c0); %the number of lakes
+
+% The volumes of lakes in km^3
+V = ones(1,n);
+V = [1, 2, 3, 4, 5, 6];
+
+% The loop of channels. 
+% Lake 1 feeds into Lake 2, which feeds into Lake 3, etc...
+r = diag(ones(1,n-1),-1);
+r(1,n) = 1;
+r = 1e-2 * r;
+
+R = sum(r);
+
+%Build the ODE matrix  
+%(note: there are more efficient ways to do this, but this one is simple & readable)
+A = r;
+for i=1:n
+    A(i,i) = - R(i);
+    A(i,:) = A(i,:) / V(i);
+end
+
+amplitude = 1;
+t_star = 300;  %after how many days will we check the concentrations?
+
+%specify some accuracy requirements for the ode solvers
+odeopt = odeset('AbsTol', 1e-6, 'RelTol', 1e-12);
+c_ode = @(t, c) (2+amplitude*sin(2*pi*t/100)) * A*c;
+
+[t,cc] = ode45(c_ode, [0:t_star], c0, odeopt);
+% close all;
+plot(t,cc);
+legend('Lake 1', 'Lake 2', 'Lake 3', 'Lake 4', 'Lake 5', 'Lake 6');
+xlabel('t'); ylabel('c');
+
+% let's experimentally test the linear superposition principle when 
+% coefficients are time-dependent
+cc_alternative=zeros(size(cc));
+for i=1:n
+    e = zeros(n,1);
+    e(i) = 1;
+    [t,w] = ode45(c_ode,[0:t_star], e, odeopt);
+
+    cc_alternative = cc_alternative + c0(i)*w;
+end
+difference = norm(cc_alternative-cc)
+% small difference ==> superposition works
+

### 2015-11-14 lakes/lakes_solved.m

@@ -1,0 +1,59 @@
+% initial concentrations of chemicals in each lake
+c0 = [1;0;1;0;0;0];
+amplitude=1;
+
+n = length(c0); %the number of lakes
+
+% The volumes of lakes in km^3
+V = [1,2,3,4,5,6];
+r = diag(ones(1,n-1),-1);
+r(1,n) = 1;
+r = 1e-2 * r;
+
+R = sum(r);
+
+% Build the ODE matrix  
+% (note: there are more efficient ways to do this, but this one is simple & readable)
+A = r;
+for i=1:n
+    A(i,i) = - R(i);
+    A(i,:) = A(i,:) / V(i);
+end
+
+t_star = 300;  %after how many days will we check the concentrations?
+
+
+% specify some accuracy requirements for the ode solvers
+odeopt = odeset('AbsTol', 1e-6, 'RelTol', 1e-12);
+
+[t,cc]=ode45(@(t,c) (2+amplitude*sin(2*pi*t/100)) * A*c, [0:t_star], c0, odeopt);
+plot(t,cc);
+legend('Lake 1', 'Lake 2', 'Lake 3', 'Lake 4', 'Lake 5', 'Lake 6');
+xlabel('t');
+ylabel('c');
+
+%let's experimentally test the linear superposition principle when 
+%coefficients are time-dependent
+cc_alternative=zeros(size(cc));
+wvector = zeros(n,n);
+for i=1:n
+    %prepare the special initial conditions
+    e = zeros(n,1);
+    e(i) = 1;
+    %find the corresponding solution
+    [t,w]=ode45(@(t,c) (2+amplitude*sin(2*pi*t/100)) * A*c,[0:t_star], e, odeopt);
+    % note that this w is what we called w^i in the lecture
+    wvector(i,:) = w(end, :);
+    cc_alternative = cc_alternative + c0(i)*w;
+end
+difference = norm(cc_alternative-cc);
+
+f = [V]; 
+Constraint = [-wvector(:,6)'; wvector(:,6)'; wvector(:,1)'; -wvector(:,1)'; wvector(:,2)'; -wvector(:,2)';...
+    wvector(:,3)'; -wvector(:,3)'; wvector(:,4)'; -wvector(:,4)'; wvector(:,5)'; -wvector(:,5)'];
+bounds = [-.4; .4; .4; -.3; .4; -.3; .4; -.3; .4; -.3; .4; -.3];
+LB = [0 0 0 0 0 0];
[…]

### 2015-11-14 get_adjacency.py
Added matlab converter

@@ -36,7 +36,7 @@ def maxpair(p):
     return max(p[:2])
 
 def to_matlab(mat):
-    s = '['
+    s = 'm = ['
     for row in mat:
         s += str(row) + ';'
 

### 2015-11-14 mat.m
Printing out adjacency seems to work

@@ -1,0 +1,1 @@
+m = [1 2 3]

### 2015-11-14 mat.m
Generating mat works

@@ -1,1 +1,2 @@
-m = [1 2 3]
+m = [[0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 2, 0, 0, 0];[0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 2, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 2, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0];[0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0];[0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 2, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0,
[…]

### 2015-11-15 stochastic/graph.py
Moar data

@@ -1,0 +1,2 @@
+class Node:
+    def __init__(self, north, west, population)

### 2015-11-15 stochastic/wolfram.py

@@ -1,0 +1,50 @@
+#!/usr/bin/python
+
+url = "http://api.wolframalpha.com/v2/query?appid=X58777-QPLTKWGKEH&input={county}%20County,%20Mississippi%20(US%20county)"
+query = "{county} County, Mississippi  (US county)"
+
+def save_location_dict(d):
+    from pickle import dump
+    dump(d, open('county_locations.dict', 'wb'))
+
+def load_location_dict():
+    from pickle import load
+    from os.path import exists
+    if exists('county_locations.dict'):
+        return load(open('county_locations.dict', 'r'))
+    else:
+        locations = get_county_locations()
+        save_location_dict(locations)
+        return locations
+
+def parse_url(google_maps):
+    coords = google_maps[google_maps.find("amp;q=")+len("amp;q="):].replace('%20','').replace('%2C',',').replace('N','').replace('W','').replace('S','').replace('E','')
+    north, west = map(lambda f:abs(float(f)), coords.split(','))
+    return north, west
+
+def get_county_location(county):
+    from urllib2 import urlopen
+    page = urlopen(url.format(county = county.replace(' ','%20'))).read()
+    u = page.find("http://maps.google.com")
+    google_maps = page[u:u + page[u:].find("'")]
+    print google_maps
+    return parse_url(google_maps)
+
+def read_counties():
+    ls = []
+    with open('../mississippi_county.list','r') as f:
+        for county in f.read().split('\n'):
+            ls += [county]
+    return ls
+
+def get_county_locations():
+    locations = dict()
+    for county in read_counties:
+        while True:
+            try: # lol
+                locations[county] = get_county_location(county)
+                break
+            except:
+                pass
+    return locations
+

### 2015-11-15 stochastic/graph.py
Fixed filenames

@@ -1,2 +1,3 @@
-class Node:
-    def __init__(self, north, west, population)
+class County:
+    def __init__(self, location, population, neighbors):
+        self.location =

### 2015-11-15 stochastic/graph.py
Yee, cleaned up the thing

@@ -1,3 +1,24 @@
+from wolfram import load_location_dict
+
 class County:
-    def __init__(self, location, population, neighbors):
-        self.location =
+    def __init__(self, county, location, population, neighbors):
+        self.county = county
+        self.location = location
+        self.population = population
+        self.neighbors = neighbors
+
+out_of_states = [('OOS1',82),('OOS2',83),('OOS3',84),('OOS4',85),('OOS5',86),('OOS6',87)]
+
+def load_highways():
+    with open('../mississippi_county.list','r') as f:
+        counties = dict(map(lambda (x,y): (y,x), enumerate(f.readlines())) + out_of_states)
+    highways = dict()
+    for line in open('../mississippi_graph.csv'):
+        line = line.strip().split(',')
+        highways[(line[0],line[1])] = int(line[2])
+    return highways
+
+if __name__ == '__main__':
+    k = load_highways()
+    left = set(filter(lambda (x,y): x < y, k))
+    right = set(map(lambda (x,y): (y,x), filter(lambda (x,y): x > y, k)))

### 2015-11-15 manuscript.tex
Added source to manuscript
done researching hurricanes; starting code

@@
-\documentclass{article}
+\documentclass[titlepage]{article}
 % \usepackage[margin=2.5cm]{geometry}
@@
 
-\title{Exit Strategy}
-\author{Paul Chesnais, Antoine Pourchet and Ryan Vogan}
-\date{\today}
+\title{Hurricane Evacuation Strategies for the State of Mississippi}
+\author{A submission for the 2015 Cornell Mathematical Contest in Modeling \\ Prepared by Paul Chesnais, Antoine Pourchet and Ryan Vogan}
+\date{November 16, 2015}
 
@@
 \lhead{Chesnais, Pourchet, Vogan}
-\chead{Exit Strategy}
+\chead{Hurricane Evacuation Strategies}
 \rhead{\today}
@@
     \url{http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4060166/}
+  \bibitem{ms_highways}
+    \url{https://www.mississippi.org/assets/docs/library/ms_highways.pdf}
 \end{thebibliography}

### 2015-11-15 get_adjacency.py
Moved stuff to utils

@@ -1,16 +1,7 @@
 #! /usr/bin/python
 
 import csv
-
-def get_name_map(filename):
-    with open(filename, 'rb') as fh:
-        h = {}
-        counter = 0
-        for line in fh:
-            h[line.strip()] = counter
-            counter += 1
-
-        return h
+import utils
 
 def get_pairs(filename, names):
     with open(filename, 'rb') as csvfile:
@@ -36,17 +27,10 @@ def get_adjacency(pairs):
 def maxpair(p):
     return max(p[:2])
 
-def to_matlab(mat):
-    s = 'm = ['
-    for row in mat:
-        s += str(row) + ';'
-
-    return s + ']'
-
 if __name__ == "__main__":
-    names = get_name_map("mississippi_county.list")
+    names = utils.get_name_map("mississippi_county.list")
     pairs = get_pairs("mississippi_graph_NS.csv", names)
     mat = get_adjacency(pairs)
-    s = to_matlab(mat)
+    s = utils.to_matlab(mat)
     print s
 

### 2015-11-15 utils.py

@@ -1,0 +1,28 @@
+#! /usr/bin/python
+
+import csv
+
+def get_name_map(filename):
+    with open(filename, 'rb') as fh:
+        h = {}
+        counter = 0
+        for line in fh:
+            h[line.strip()] = counter
+            counter += 1
+
+        return h
+
+def to_matlab(mat):
+    s = 'm = ['
+    for row in mat:
+        s += str(row) + ';'
+
+    return s + ']'
+
+if __name__ == "__main__":
+    names = get_name_map("mississippi_county.list")
+    pairs = get_pairs("mississippi_graph_NS.csv", names)
+    mat = get_adjacency(pairs)
+    s = to_matlab(mat)
+    print s
+

### 2015-11-15 deterministic/adjacency.m
Changed a bunch of shit

@@ -1,0 +1,83 @@
+adj = [[0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 2, 0, 0, 0];
+[0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 2, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 2, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0];
+[0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0];
[…]

### 2015-11-15 deterministic/constantrate.m

@@ -1,0 +1,24 @@
+populations % pops
+adjacency % adj
+adj = 0.01 * adj;
+
+% pops = [100; 10; 10];
+% adj = [ 0, 0, 0; 0.1, 0, 0; 0, 0.1, 0; ];
+
+R = sum(adj);
+
+A = adj;
+for i=1:length(A)
+    A(i,i) = 1-R(i);
+end
+
+curr_pop = pops;
+interest = [];
+max_t = 3000;
+for t=0:1:max_t
+    interest = [interest curr_pop(5)];
+    curr_pop = A * curr_pop;
+end
+
+figure
+plot(interest)

### 2015-11-15 get_adjacency.py

@@ -21,6 +21,7 @@ def get_adjacency(pairs):
     mat = [[0 for a in range(matsize)] for a in range(matsize)]
     for p in pairs:
         mat[p[1]][p[0]] = p[2]
+        # mat[p[0]][p[1]] = -p[2]
 
     return mat
 
@@ -31,6 +32,6 @@ if __name__ == "__main__":
     names = utils.get_name_map("mississippi_county.list")
     pairs = get_pairs("mississippi_graph_NS.csv", names)
     mat = get_adjacency(pairs)
-    s = utils.to_matlab(mat)
+    s = utils.to_matlab(mat, 'adj')
     print s
 

### 2015-11-15 get_pop.py

@@ -1,0 +1,16 @@
+#! /usr/bin/python
+
+import utils
+
+def get_mat(names, population):
+    mat = []
+    for t in population:
+        mat.append(t[1])
+    return mat
+
+if __name__ == "__main__":
+    populations = utils.get_population("mississippi_county_pop.csv")
+    names = utils.get_name_map("mississippi_county.list")
+    mat = get_mat(names, populations)
+    s = utils.to_matlab(mat, 'pops')
+    print s

### 2015-11-15 utils.py

@@ -2,6 +2,16 @@
 
 import csv
 
+def get_population(filename):
+    with open(filename, 'rb') as fh:
+        r = csv.DictReader(fh)
+        pairs = []
+        for row in r:
+            t = (row['NAME'], int(row['POPULATION']))
+            pairs.append(t)
+
+        return pairs
+
 def get_name_map(filename):
     with open(filename, 'rb') as fh:
         h = {}
@@ -12,17 +22,10 @@ def get_name_map(filename):
 
         return h
 
-def to_matlab(mat):
-    s = 'm = ['
+def to_matlab(mat, mname = 'm'):
+    s = mname + ' = ['
     for row in mat:
-        s += str(row) + ';'
+        s += str(row) + ';\n'
 
-    return s + ']'
-
-if __name__ == "__main__":
-    names = get_name_map("mississippi_county.list")
-    pairs = get_pairs("mississippi_graph_NS.csv", names)
-    mat = get_adjacency(pairs)
-    s = to_matlab(mat)
-    print s
+    return s + '];'
 

### 2015-11-15 stochastic/data.py
County pop

@@ -1,0 +1,36 @@
+#!/usr/bin/python
+
+from wolfram import load_location_dict
+
+county_map = dict()
+highways = dict()
+locations = dict()
+populations = dict()
+
+pphpr = 3000 # People per hour per unit of road
+
+def load_highways():
+    global county_map
+    global highways
+    out_of_states = [('OOS1',82),('OOS2',83),('OOS3',84),('OOS4',85),('OOS5',86),('OOS6',87)]
+    with open('../mississippi_county.list') as f:
+        county_map = dict(map(lambda (x,y): (y.strip(),x), enumerate(f.readlines())) + out_of_states)
+    for line in open('../mississippi_graph.csv'):
+        c1,c2,cap = line.strip().split(',')
+        highways[(county_map[c1], county_map[c2])] = int(cap)
+
+def load_locations():
+    global locations
+    out_of_states_locations = {'OOS1': (1,1), 'OOS2': (1,1), 'OOS3': (1,1), 'OOS4': (1,1), 'OOS5': (1,1), 'OOS6': (1,1)}
+    locs = dict(load_location_dict().items() + out_of_states_locations.items())
+    locations = dict(map(lambda c: (county_map[c], locs[c]), locs))
+
+def load_populations():
+    global populations
+    for line in open('../mississippi_county_pop.csv'):
+        county, pop = line.strip().split(',')
+        populations[county_map[county]] = pop
+
+load_highways()
+load_locations()
+load_populations()

### 2015-11-15 stochastic/graph.py

@@ -1,24 +1,0 @@
-from wolfram import load_location_dict
-
-class County:
-    def __init__(self, county, location, population, neighbors):
-        self.county = county
-        self.location = location
-        self.population = population
-        self.neighbors = neighbors
-
-out_of_states = [('OOS1',82),('OOS2',83),('OOS3',84),('OOS4',85),('OOS5',86),('OOS6',87)]
-
-def load_highways():
-    with open('../mississippi_county.list','r') as f:
-        counties = dict(map(lambda (x,y): (y,x), enumerate(f.readlines())) + out_of_states)
-    highways = dict()
-    for line in open('../mississippi_graph.csv'):
-        line = line.strip().split(',')
-        highways[(line[0],line[1])] = int(line[2])
-    return highways
-
-if __name__ == '__main__':
-    k = load_highways()
-    left = set(filter(lambda (x,y): x < y, k))
-    right = set(map(lambda (x,y): (y,x), filter(lambda (x,y): x > y, k)))

### 2015-11-15 hurricane_generator/geography.py
hurricane code

@@ -1,0 +1,25 @@
+from urllib2 import urlopen
+import json
+import time
+def geo_tag(lat, lon, delay=1):
+    url = "https://maps.googleapis.com/maps/api/geocode/json?"
+    url += "latlng=%s,%s&sensor=false" % (lat, lon)
+    url += "&key=AIzaSyAe_x2u6tRdLob41KRAvLw6b91MQ3W0NxI"
+    try:
+        v = urlopen(url).read()
+    except:
+        print "RECONNECT"
+        time.sleep(delay)
+        return geo_tag(lat, lon, delay + 1)
+    j = json.loads(v)
+    state = county = None
+    if len(j['results']) > 0:
+        components = j['results'][0]['address_components']
+        for c in components:
+            if "administrative_area_level_1" in c['types']:
+                state = c['long_name']
+            if "administrative_area_level_2" in c['types']:
+                county = c['long_name']
+    return (county,state)
+
+# print geo_tag(40.1308,-75.5192)

### 2015-11-15 hurricane_generator/geography.py
Fixing hurricane generator bad requests

@@ -5,9 +5,11 @@ def geo_tag(lat, lon, delay=1):
     url = "https://maps.googleapis.com/maps/api/geocode/json?"
     url += "latlng=%s,%s&sensor=false" % (lat, lon)
     url += "&key=AIzaSyAe_x2u6tRdLob41KRAvLw6b91MQ3W0NxI"
+    print url
     try:
         v = urlopen(url).read()
-    except:
+    except Exception as e:
+        print e
         print "RECONNECT"
         time.sleep(delay)
         return geo_tag(lat, lon, delay + 1)

### 2015-11-15 hurricane_generator/reverse_geotag.py

@@ -19,9 +19,9 @@ while row < num_rows:
 	if data.ix[row][0][0:2] == 'AL':
 		row = row + 1
 		pass
-	latitude = data.ix[row][4][1:5]
+	latitude = data.ix[row][4][1:5].strip()
 	print latitude
-	longitude = "-" + data.ix[row][5][2:6]
+	longitude = "-" + data.ix[row][5][2:6].strip()
 	print longitude
 	(county,state) = geo_tag(latitude, longitude)
 	if county != None:

### 2015-11-15 deterministic/constantflat.m
Matlab is CANCER

@@ -1,0 +1,31 @@
+populations % pops
+adjacency % adj
+
+% pops = [100; 10; 10];
+% adj = [ 0, 0, 0; 0.1, 0, 0; 0, 0.1, 0; ];
+
+orig_adj = adj;
+for i=1:length(adj)
+    adj(:,i) = adj(:,i) * 3000 / pops(i);
+end
+
+A = getA(adj);
+
+curr_pop = pops;
+interests = [];
+max_t = 97;
+for t=0:1:max_t
+    for i=1:length(adj)
+        adj(:,i) = orig_adj(:,i) * 3000 / max(0.01, curr_pop(i));
+        s = sum(adj);
+        if s(i) > 1
+            adj(:,i) = adj(:, i) / s(i);
+        end
+    end
+    A = getA(adj);
+    interests = [interests; (curr_pop ./ pops)'];
+    curr_pop = A * curr_pop;
+end
+
+figure
+plot(interests(:,30))

### 2015-11-15 deterministic/constantflat.m
added certainties

@@ -7,6 +7,10 @@ adjacency % adj
 orig_adj = adj;
 for i=1:length(adj)
     adj(:,i) = adj(:,i) * 3000 / pops(i);
+    s = sum(adj);
+    if s(i) > 0.95
+        adj(:,i) = adj(:, i) * 0.95 / s(i);
+    end
 end
 
 A = getA(adj);

### 2015-11-15 deterministic/constantrate.m

@@ -6,6 +6,10 @@ adjacency % adj
 
 for i=1:length(adj)
     adj(:,i) = adj(:,i) * 3000 / pops(i);
+    s = sum(adj);
+    if s(i) > 0.95
+        adj(:,i) = adj(:, i) * 0.95 / s(i);
+    end
 end
 R = sum(adj);
 
@@ -22,5 +26,5 @@ for t=0:1:max_t
     curr_pop = A * curr_pop;
 end
 
-% figure
-% plot(interest(:,30))
+figure
+plot(interest(:,30))

### 2015-11-15 hurricane_generator/geography.py
geotagging done

@@ -5,12 +5,10 @@ def geo_tag(lat, lon, delay=1):
     url = "https://maps.googleapis.com/maps/api/geocode/json?"
     url += "latlng=%s,%s&sensor=false" % (lat, lon)
     url += "&key=AIzaSyAe_x2u6tRdLob41KRAvLw6b91MQ3W0NxI"
-    print url
     try:
         v = urlopen(url).read()
     except Exception as e:
         print e
-        print "RECONNECT"
         time.sleep(delay)
         return geo_tag(lat, lon, delay + 1)
     j = json.loads(v)

### 2015-11-15 hurricane_generator/reverse_geotag.py

@@ -13,7 +13,7 @@ num_rows = data.shape[0]
 
 open('geo_tags.csv', 'w').close()
 
-row = 1450
+row = 1462
 while row < num_rows:
 	print "Row: " + str(row)
 	if data.ix[row][0][0:2] == 'AL':

### 2015-11-15 hurricane_generator/geotag.py
geotag outputting done

@@ -5,15 +5,36 @@ import sys    # sys.setdefaultencoding is cancelled by site.py
 reload(sys)    # to re-enable sys.setdefaultencoding()
 sys.setdefaultencoding('utf-8')
 
-
-from geography import geo_tag
+from urllib2 import urlopen
+import json
+import time
+def geo_tag(lat, lon, delay=1):
+    url = "https://maps.googleapis.com/maps/api/geocode/json?"
+    url += "latlng=%s,%s&sensor=false" % (lat, lon)
+    url += "&key=AIzaSyAe_x2u6tRdLob41KRAvLw6b91MQ3W0NxI"
+    try:
+        v = urlopen(url).read()
+    except Exception as e:
+        print e
+        time.sleep(delay)
+        return geo_tag(lat, lon, delay + 1)
+    j = json.loads(v)
+    state = county = None
+    if len(j['results']) > 0:
+        components = j['results'][0]['address_components']
+        for c in components:
+            if "administrative_area_level_1" in c['types']:
+                state = c['long_name']
+            if "administrative_area_level_2" in c['types']:
+                county = c['long_name']
+    return (county,state)
 
 data = pd.read_csv('hurdat2.csv', dtype = str)
 num_rows = data.shape[0]
 
-open('geo_tags.csv', 'w').close()
+open('geo_tag_output.csv', 'w').close()
 
-row = 1462
+row = 1461
 while row < num_rows:
 	print "Row: " + str(row)
 	if data.ix[row][0][0:2] == 'AL':

### 2015-11-15 stochastic/data.py
Pushed before going to airport. Working a bit

@@ -1,13 +1,65 @@
 #!/usr/bin/python
 
 from wolfram import load_location_dict
+from numpy import vdot, arccos, degrees, mean
+from numpy.linalg import norm
+
+class LonLat:
+    def __init__(self, lon, lat):
+        self.lon = lon
+        self.lat = lat
+
+    def away_from_hurricane(self, current_position, hurricane_pos):
+        v1 = [current_position.lon - hurricane_pos.lon, current_position.lat - hurricane_pos.lat]
+        v2 = [self.lon - current_position.lon, self.lat - current_position.lat]
+        return abs(degrees(arccos(vdot(v1,v2)/(norm(v1)*norm(v2))))) < 90
+
+class County:
+    def __init__(self, id):
+        self.id = id
+
+    def get_neighbors(self):
+        return neighbor_map[self.id]
+
+    def viable_neighbors(self, hurricane_loc):
+        neighbors = self.get_neighbors()
+        return filter(lambda id: locations[id].away_from_hurricane(locations[self.id], hurricane_loc), neighbors)
+
+    def get_county_name(self):
+        return filter(lambda k: county_map[k] == self.id, county_map)[0]
+
+    def decrease_pop(self):
+        populations[self.id] -= pphpr
+
+    def increase_pop(self):
+        populations[self.id] += pphpr
+
+    def escape(self, hurricane_loc, highway_quotas):
+        neighbors = self.viable_neighbors(hurricane_loc)
+        quotas = map(lambda id: (id, highway_quotas[ordered_tuple(self.id, id)]), neighbors)
+        print quotas
+        best_route = max(quotas, key = lambda (id, quota): quota)
+        if best_route[1] > 0:
+            highway_quotas[ordered_tuple(best_route[0], self.id)] -= 1
+            self.decrease_pop()
+            County(best_route[0]).increase_pop()
 
 county_map = dict()
 highways = dict()
 locations = dict()
 populations = dict()
+neighbor_map = dict()
 
 pphpr = 3000 # People per hour per unit of road
+
+def ordered_tuple(k1,k2): return min(k1,k2),max(k1,k2)
+
+def average_huricane_counties(hurricane_counties):
+    if type(hurricane_counties[0]) == type(''):
+            hurricane_counties = map(lambda s: locations[county_map[s]], hurricane_counties)
+    elif type(hurricane_counties[0]) == type(1):
[…]

### 2015-11-15 stochastic/simulation.py

@@ -1,0 +1,29 @@
+#!/usr/bin/python
+
+from sys import argv
+from data import County, county_map, average_huricane_counties, highways
+
+hours = -4*24
+
+highway_quotas = dict()
+
+def flatten(l): return [item for sublist in l for item in sublist]
+
+def main(predictions):
+    global highway_quotas
+    hurricanes = map(average_huricane_counties, predictions)
+
+    times = [2*24, 24, 24]
+
+    for stage in range(0,3):
+        for _ in range(times[stage]):
+            highway_quotas = highways.copy()
+            second_degree_neighbors = set(flatten(map(lambda id: County(id).get_neighbors(), predictions[stage])))
+            for neighbor in second_degree_neighbors:
+                print neighbor
+                County(neighbor).escape(hurricanes[stage], highway_quotas)
+
+if __name__ == '__main__':
+    with open(argv[1]) as f:
+        args = map(lambda line: map(lambda c: county_map[c], line.strip().split(',')), f.readlines())
+    main(args)

### 2015-11-15 manuscript.tex

@@
 \title{Hurricane Evacuation Strategies for the State of Mississippi}
-\author{A submission for the 2015 Cornell Mathematical Contest in Modeling \\ Prepared by Paul Chesnais, Antoine Pourchet and Ryan Vogan}
-\date{November 16, 2015}
+\author{Paul Chesnais (pmc85), Antoine Pourchet (app63), and Ryan Vogan (rcv39)\\2015 Cornell Mathematical Contest in Modeling\\November 16, 2015}
+\date{}
 
@@
 
-\section{Abstract}
-\label{sec:abstract}
+\section{Executive Summary}
+\label{sec:summary}
 
-\section{Executive Summary}
-\label{sec:executive_summary}
+\section{Introduction}
+\label{sec:introduction}
 
-% Antoine's stuff and thing
-\section{Deterministic Model}
-\label{sec:deterministic_model}
+\section{Model Assumptions}
+\label{sec:assumptions}
 
-% Paul's stuff and things
-\section{Stochastic Model}
-\label{sec:stochastic_model}
+\section{Statical Analysis of Historical Hurricane Data}
+\label{sec:hurricanes}
 
+\section{Markov Process Analysis of Strictly Northern Evacuations}
+\label{sec:markov}
+  \subsection{Model Description}
+  \subsection{Parameter Values and Justification}
+  \subsection{Results}
+  \subsection{Strengths and Weaknesses}
+
+\section{Maximum Flow Analysis of Strictly Northern Evacuations}
+\label{sec:maxflow}
+  \subsection{Model Description}
+  \subsection{Parameter Values and Justification}
+  \subsection{Results}
+  \subsection{Strengths and Weaknesses}
+
+\section{Stochastic Model of Landfall-Avodiant Evacuations}
+\label{sec:stochastic}
+  \subsection{Model Description}
+  \subsection{Parameter Values and Justification}
+  \subsection{Results}
+  \subsection{Strengths and Weaknesses}
+
+\section{Conclusions}
+\label{sec:conclusions}
+
+\section{Future Work}
+\label{sec:future}
+
+\section{Individual Contributions}
+\label{sec:contributions}
   \begin{thebibliography}{9}

### 2015-11-16 hurricane_generator/clean.py
starting to get radii

@@ -1,52 +1,48 @@
 import pandas as pd
 import numpy as np
 
-import time
-
-from geography import get_state
-
 data = pd.read_csv('hurdat2.csv', dtype = str)
+geotags = pd.read_csv('geotags.csv', dtype = str)
 num_rows = data.shape[0]
 
 open('hurdat2_cleaned.csv', 'w').close()
 
 row = 0
+reading = 1
 num_hurricanes = 0
 
 def skip_to_next_hurricane():
 	global row
+	global reading
 	global num_hurricanes
 	while row < num_rows and data.ix[row][0][0:2] != 'AL':
 		row = row + 1
+		reading = reading + 1
 	row = row + 1
 	num_hurricanes = num_hurricanes + 1
-	if row < num_rows:
-		print "\r\nHurricane " + str(num_hurricanes) + "/1793"
 
 skip_to_next_hurricane()
 while row < num_rows:
 	if data.ix[row][0][0:2] == 'AL':
 		row = row + 1
 		num_hurricanes = num_hurricanes + 1
-		if row < num_rows:
-			print "\r\nHurricane " + str(num_hurricanes) + "/1793"
-		pass
-	latitude = data.ix[row][4][1:5]
-	longitude = "-" + data.ix[row][5][2:6]
-	state = get_state(latitude, longitude)
-	if state != None:
-		print state
-	else:
-		print "Ocean"
-	if state == "Mississippi" and data.ix[row][3] == "HU":
+	assert geotags.ix[reading-1][0] == str(row)
+	latitude = geotags.ix[reading-1][1]
+	longitude = geotags.ix[reading-1][2]
+	county = geotags.ix[reading-1][3]
+	state = geotags.ix[reading-1][4]
+	if state == "Mississippi" and data.ix[row][3].strip() == "HU":
+		print data.ix[row][3]
 		fileStream = open('hurdat2_cleaned.csv','a')
-		fileStream.write(latitude + "," + longitude + ",")
-		fileStream.write(get_county(latitude, longitude) + ",")
+		fileStream.write(latitude + ",")
+		fileStream.write(longitude + ",")
+		fileStream.write(county + ",")
 		fileStream.write(data.ix[row][6] + ",")
-		fileStream.write(str(mean(int(data.ix[row][8:12]))) + ",")
-		fileStream.write(str(mean(int(data.ix[row][12:16]))) + ",")
[…]

### 2015-11-16 stochastic/data.py
Def on the right track to have something that works

@@ -9,6 +9,12 @@ class LonLat:
         self.lon = lon
         self.lat = lat
 
+    def __str__(self):
+        return "(%0.5F,%0.5F)"%(self.lon,self.lat)
+
+    def __repr__(self):
+        return "LonLat(%0.5F,%0.5F)"%(self.lon,self.lat)
+
     def away_from_hurricane(self, current_position, hurricane_pos):
         v1 = [current_position.lon - hurricane_pos.lon, current_position.lat - hurricane_pos.lat]
         v2 = [self.lon - current_position.lon, self.lat - current_position.lat]
@@ -17,16 +23,21 @@ class LonLat:
 class County:
     def __init__(self, id):
         self.id = id
+        self.out_of_state = id > 82
 
-    def get_neighbors(self):
-        return neighbor_map[self.id]
+    def __str__(self): return "County(%s|%d)"%(self.get_county_name(), self.id)
+
+    def __repr__(self): return "County(%s|%d)"%(self.get_county_name(), self.id)
+
+    def get_location(self): return locations[self.id]
+
+    def get_county_name(self): return filter(lambda k: county_map[k] == self.id, county_map)[0]
+
+    def get_neighbors(self): return neighbor_map[self.id]
 
     def viable_neighbors(self, hurricane_loc):
         neighbors = self.get_neighbors()
         return filter(lambda id: locations[id].away_from_hurricane(locations[self.id], hurricane_loc), neighbors)
-
-    def get_county_name(self):
-        return filter(lambda k: county_map[k] == self.id, county_map)[0]
 
     def decrease_pop(self):
         populations[self.id] -= pphpr
@@ -64,9 +75,9 @@ def average_huricane_counties(hurricane_counties):
 def load_highways():
     global county_map
     global highways
-    out_of_states = [('OOS1',82),('OOS2',83),('OOS3',84),('OOS4',85),('OOS5',86),('OOS6',87)]
+    out_of_state = [('OOS1',82),('OOS2',83),('OOS3',84),('OOS4',85),('OOS5',86),('OOS6',87)]
     with open('../mississippi_county.list') as f:
-        county_map = dict(map(lambda (x,y): (y.strip(),x), enumerate(f.readlines())) + out_of_states)
+        county_map = dict(map(lambda (x,y): (y.strip(),x), enumerate(f.readlines())) + out_of_state)
[…]

### 2015-11-16 stochastic/simulation.py

@@ -12,18 +12,26 @@ def flatten(l): return [item for sublist in l for item in sublist]
 def main(predictions):
     global highway_quotas
     hurricanes = map(average_huricane_counties, predictions)
-
+    print hurricanes
     times = [2*24, 24, 24]
 
     for stage in range(0,3):
         for _ in range(times[stage]):
             highway_quotas = highways.copy()
             second_degree_neighbors = set(flatten(map(lambda id: County(id).get_neighbors(), predictions[stage])))
+            second_degree_neighbors = filter(lambda c: not County(c).out_of_state, second_degree_neighbors)
             for neighbor in second_degree_neighbors:
                 print neighbor
                 County(neighbor).escape(hurricanes[stage], highway_quotas)
 
 if __name__ == '__main__':
-    with open(argv[1]) as f:
-        args = map(lambda line: map(lambda c: county_map[c], line.strip().split(',')), f.readlines())
+    global args
+    if len(argv) > 2:
+        with open(argv[1]) as f:
+            args = map(lambda line: map(lambda c: county_map[c], line.strip().split(',')), f.readlines())
+    else:
+        args = [map(lambda c: county_map[c], ['Hancock','PearlRiver','Harrison','Jackson','Stone','George','Marion','Lamar','Forrest','Perry','Greene']),
+                map(lambda c: county_map[c], ['Hancock','PearlRiver','Harrison','Jackson','Stone','George']),
+                map(lambda c: county_map[c], ['Hancock','Harrison','Jackson'])]
     main(args)
+

### 2015-11-16 stochastic/wolfram.py

@@ -19,8 +19,8 @@ def load_location_dict():
 
 def parse_url(google_maps):
     coords = google_maps[google_maps.find("amp;q=")+len("amp;q="):].replace('%20','').replace('%2C',',').replace('N','').replace('W','').replace('S','').replace('E','')
-    north, west = map(lambda f:abs(float(f)), coords.split(','))
-    return north, west
+    north, east = map(lambda f:abs(float(f)), coords.split(','))
+    return north, -east
 
 def get_county_location(county):
     from urllib2 import urlopen

### 2015-11-16 flow/maxflow.py
dope titties

@@ -2,37 +2,65 @@
 import utils
 from graph_tool.all import *
 import graph_tool.flow as gt
+import pickle as pk
+
 
 if __name__ == "__main__":
+    positions = pk.load(open("county_locations.dict"))
+    positions = sorted(positions.items(), key=lambda (k, v) : k)
+    positions = map(lambda (k, v) : (v[1], v[0]), positions)
+
     names = utils.get_name_map("../mississippi_county.list")
     edges = utils.get_edges("../mississippi_graph_NS.csv", names)
+
     g = Graph()
     g.set_directed(True)
     source = g.add_vertex()
     vertices = g.add_vertex(len(names))
     sink = g.add_vertex()
     cap = g.new_edge_property("double")
+    pos = g.new_vertex_property("vector<double>")
+    edge_cap_text = g.new_edge_property("string")
+
+    pos[0] = [-90, -29.7]
+    pos[len(positions) + 1] = [-90, -36]
+    for p in range(len(positions)):
+        (x, y) = positions[p]
+        pos[p+1] = [x, -y]
+        p += 1
+
     for e in edges:
-        edge = g.add_edge(e[0]+1, e[1])
+        edge = g.add_edge(e[0]+1, e[1]+1)
         cap[edge] = e[2]
+        edge_cap_text[edge] = str(e[2])
 
     bottom_states = [23, 24, 30, 46, 74, 57, 3, 79]
-    top_states = [17, 47, 5, 70, 2, 71]
+    top_states = [17, 47, 5, 70, 2, 71, 14, 72]
     for i in bottom_states:
         e = g.add_edge(0, i)
-        cap[e] = 10000
+        cap[e] = 7
 
     for i in top_states:
         e = g.add_edge(i, len(names)+1)
-        cap[e] = 10000
+        cap[e] = 7
 
     res = gt.boykov_kolmogorov_max_flow(g, source, sink, cap)
     part = gt.min_st_cut(g, source, cap, res)
     mc = sum([cap[e] - res[e] for e in g.edges() if part[e.source()] != part[e.target()]])
-    # mc, part = gt.min_cut(g, cap)
-    print(mc)
-
     res.a = cap.a - res.a  # the actual flow
-    gt.graph_draw(g, pos=pos, edge_pen_width=gt.prop_to_size(cap, mi=3, ma=10, power=1),
-            edge_text=res, vertex_fill_color=part, vertex_text=g.vertex_index,
[…]

### 2015-11-16 hurricane_generator/geotag.py
all

@@ -32,7 +32,7 @@ def geo_tag(lat, lon, delay=1):
 data = pd.read_csv('hurdat2.csv', dtype = str)
 num_rows = data.shape[0]
 
-open('geo_tag_output.csv', 'w').close()
+open('geotag_output.csv', 'w').close()
 
 row = 1461
 while row < num_rows:

### 2015-11-16 hurricane_generator/get_radii.py

@@ -1,0 +1,23 @@
+import pandas as pd
+import numpy as np
+
+data = pd.read_csv('hurdat2.csv', dtype = str)
+num_rows = data.shape[0]
+
+open('wind_radii.csv', 'w').close()
+
+row = 44300
+while row < num_rows:
+	if data.ix[row][0][0:4] == '2004':
+		wind_speed = data.ix[row][6]
+		wind_radius = np.mean(map(float,data.ix[row][16:20]))
+		if not wind_radius > 0:
+			wind_radius = np.mean(map(float,data.ix[row][12:16])) 
+		if not wind_radius > 0:
+			wind_radius = np.mean(map(float,data.ix[row][8:12]))
+		if wind_radius > 0:
+			fileStream = open('wind_radii.csv','a')
+			fileStream.write(wind_speed + ",")
+			fileStream.write(str(wind_radius) + "\n")
+			fileStream.close()
+	row = row + 1

### 2015-11-16 hurricane_generator/final.py
done hurricane analysis

@@ -1,0 +1,32 @@
+import pandas as pd
+import numpy as np
+
+data = pd.read_csv('hurdat2_cleaned.csv', dtype=str, header=None)
+num_rows = data.shape[0]
+
+open('final.csv', 'w').close()
+
+for row in xrange(num_rows):
+	latitude = data.ix[row][0]
+	longitude = data.ix[row][1]
+	county = data.ix[row][2]
+	windspeed = int(data.ix[row][3])
+	if windspeed >= 64 and windspeed <= 82:
+		category = 1
+	elif windspeed >= 83 and windspeed <= 95:
+		category = 2
+	elif windspeed >= 96 and windspeed <= 112:
+		category = 3
+	elif windspeed >= 113 and windspeed <= 136:
+		category = 4
+	else:
+		category = 5
+	radius = round((0.4718 * windspeed - 7.6557) * 1.852)
+	fileStream = open('final.csv','a')
+	fileStream.write(latitude + ",")
+	fileStream.write(longitude + ",")
+	fileStream.write(county + ",")
+	fileStream.write(str(windspeed) + ",")
+	fileStream.write(str(category) + ",")
+	fileStream.write(str(radius) + "\n")
+	fileStream.close()

### 2015-11-16 stochastic/data.py
Should be good to go, time to get on the manu

@@ -18,16 +18,16 @@ class LonLat:
     def away_from_hurricane(self, current_position, hurricane_pos):
         v1 = [current_position.lon - hurricane_pos.lon, current_position.lat - hurricane_pos.lat]
         v2 = [self.lon - current_position.lon, self.lat - current_position.lat]
-        return abs(degrees(arccos(vdot(v1,v2)/(norm(v1)*norm(v2))))) < 90
+        return (abs(degrees(arccos(vdot(v1,v2)/(norm(v1)*norm(v2))))) < 90) #and (self.lat >= current_position.lat or self.lon >= current_position.lon)
 
 class County:
     def __init__(self, id):
         self.id = id
         self.out_of_state = id > 82
 
-    def __str__(self): return "County(%s|%d)"%(self.get_county_name(), self.id)
+    def __str__(self): return "County(%s|%d|%d)"%(self.get_county_name(),self.id, self.get_population())
 
-    def __repr__(self): return "County(%s|%d)"%(self.get_county_name(), self.id)
+    def __repr__(self): return "County(%s|%d|%d)"%(self.get_county_name(),self.id, self.get_population())
 
     def get_location(self): return locations[self.id]
 
@@ -35,25 +35,33 @@ class County:
 
     def get_neighbors(self): return neighbor_map[self.id]
 
+    def get_population(self): return populations[self.id]
+
     def viable_neighbors(self, hurricane_loc):
         neighbors = self.get_neighbors()
-        return filter(lambda id: locations[id].away_from_hurricane(locations[self.id], hurricane_loc), neighbors)
+        return filter(lambda id: locations[id].away_from_hurricane(locations[self.id], hurricane_loc) or locations[id].lat > self.get_location().lat, neighbors)
 
-    def decrease_pop(self):
-        populations[self.id] -= pphpr
-
-    def increase_pop(self):
-        populations[self.id] += pphpr
+    def move_pop(self, neighbor):
+        diff = min(pphpr, populations[self.id])
+        populations[self.id] -= diff
+        populations[neighbor] += diff
 
     def escape(self, hurricane_loc, highway_quotas):
-        neighbors = self.viable_neighbors(hurricane_loc)
-        quotas = map(lambda id: (id, highway_quotas[ordered_tuple(self.id, id)]), neighbors)
-        print quotas
-        best_route = max(quotas, key = lambda (id, quota): quota)
-        if best_route[1] > 0:
[…]

### 2015-11-16 stochastic/populations_per_hour.m

@@ -1,0 +1,96 @@
+m = [[83934,19578,26400,28929,184105,142668,58658,24088,46834,3250,8786];
+[92934,16578,32650,13929,180891,145668,61658,18531,37834,0,0];
+[101934,13578,35650,0,168891,148668,64658,6531,28834,0,0];
+[110934,10578,38650,0,156891,151668,62189,0,19834,0,0];
+[119934,9000,40228,0,144891,154668,53189,0,10834,0,0];
+[128934,9000,40228,0,132891,157668,44189,0,1834,0,0];
+[137934,9000,40228,0,120891,160668,28023,0,0,0,0];
+[146934,9000,40228,0,108891,163668,10023,0,0,0,0];
+[147957,9000,40228,0,96891,166668,0,0,0,0,0];
+[129957,9000,40228,0,84891,169668,18000,0,0,0,0];
+[138957,9000,40228,0,72891,172668,0,0,0,0,0];
+[120957,9000,40228,0,60891,175668,18000,0,0,0,0];
+[129957,9000,40228,0,48891,178668,0,0,0,0,0];
+[111957,9000,40228,0,36891,181668,18000,0,0,0,0];
+[120957,9000,40228,0,24891,184668,0,0,0,0,0];
+[102957,9000,40228,0,12891,187668,18000,0,0,0,0];
+[111957,9000,40228,0,891,190668,0,0,0,0,0];
+[93957,9000,40228,0,0,182559,18000,0,0,0,0];
+[102957,9000,40228,0,0,173559,0,0,0,0,0];
+[84957,9000,40228,0,0,164559,18000,0,0,0,0];
+[93957,9000,40228,0,0,155559,0,0,0,0,0];
+[75957,9000,40228,0,0,146559,18000,0,0,0,0];
+[84957,9000,40228,0,0,137559,0,0,0,0,0];
+[66957,9000,40228,0,0,128559,18000,0,0,0,0];
[…]

### 2015-11-16 stochastic/simulation.py

@@ -1,9 +1,7 @@
 #!/usr/bin/python
 
 from sys import argv
-from data import County, county_map, average_huricane_counties, highways
-
-hours = -4*24
+from data import County, county_map, average_huricane_counties, highways, populations
 
 highway_quotas = dict()
 
@@ -12,26 +10,33 @@ def flatten(l): return [item for sublist in l for item in sublist]
 def main(predictions):
     global highway_quotas
     hurricanes = map(average_huricane_counties, predictions)
-    print hurricanes
+    bad_counties = sorted(list(set(flatten(predictions))))
     times = [2*24, 24, 24]
 
-    for stage in range(0,3):
+    hours = list()
+    for stage in range(3):
         for _ in range(times[stage]):
             highway_quotas = highways.copy()
             second_degree_neighbors = set(flatten(map(lambda id: County(id).get_neighbors(), predictions[stage])))
             second_degree_neighbors = filter(lambda c: not County(c).out_of_state, second_degree_neighbors)
             for neighbor in second_degree_neighbors:
-                print neighbor
                 County(neighbor).escape(hurricanes[stage], highway_quotas)
+            hours.append(map(lambda c: County(c).get_population(), bad_counties))
+
+    print bad_counties
+    print map(lambda c: County(c).get_county_name(), bad_counties)
+    return hours
+
 
 if __name__ == '__main__':
-    global args
-    if len(argv) > 2:
+    if len(argv) >= 2:
         with open(argv[1]) as f:
             args = map(lambda line: map(lambda c: county_map[c], line.strip().split(',')), f.readlines())
     else:
         args = [map(lambda c: county_map[c], ['Hancock','PearlRiver','Harrison','Jackson','Stone','George','Marion','Lamar','Forrest','Perry','Greene']),
                 map(lambda c: county_map[c], ['Hancock','PearlRiver','Harrison','Jackson','Stone','George']),
                 map(lambda c: county_map[c], ['Hancock','Harrison','Jackson'])]
-    main(args)
+    hours = main(args)
 
+    s = "m = [" + ";\n".join(map(lambda h: "[" + ",".join(map(str, h)) + "]", hours)) + "]"
+    open('populations_per_hour.m', 'w').write(s)

### 2015-11-16 stochastic/data.py
More edges

@@ -86,7 +86,10 @@ def load_highways():
     out_of_state = [('OOS1',82),('OOS2',83),('OOS3',84),('OOS4',85),('OOS5',86),('OOS6',87)]
     with open('../mississippi_county.list') as f:
         county_map = dict(map(lambda (x,y): (y.strip(),x), enumerate(f.readlines())) + out_of_state)
-    for line in open('../mississippi_graph.csv'):
+    for line in open('../mississippi_graph_NS.csv'):
+        c1,c2,cap = line.strip().split(',')
+        highways[ordered_tuple(county_map[c1], county_map[c2])] = int(cap)
+    for line in open('../mississippi_graph_EW.csv'):
         c1,c2,cap = line.strip().split(',')
         highways[ordered_tuple(county_map[c1], county_map[c2])] = int(cap)
 

### 2015-11-16 stochastic/populations_per_hour.m

@@ -41,56 +41,4 @@ m = [[83934,19578,26400,28929,184105,142668,58658,24088,46834,3250,8786];
 [3957,0,24787,0,0,0,0,0,0,0,0];
 [0,0,15787,0,0,0,3957,0,0,0,0];
 [0,0,6787,0,0,0,0,0,0,0,0];
-[0,0,0,0,0,0,0,0,0,0,0];
-[0,0,0,0,0,0,0,0,0,0,0];
-[0,0,0,0,0,0,0,0,0,0,0];
-[0,0,0,0,0,0,0,0,0,0,0];
-[0,0,0,0,0,0,0,0,0,0,0];
-[0,0,0,0,0,0,0,0,0,0,0];
-[0,0,0,0,0,0,0,0,0,0,0];
-[0,0,0,0,0,0,0,0,0,0,0];
-[0,0,0,0,0,0,0,0,0,0,0];
-[0,0,0,0,0,0,0,0,0,0,0];
-[0,0,0,0,0,0,0,0,0,0,0];
-[0,0,0,0,0,0,0,0,0,0,0];
-[0,0,0,0,0,0,0,0,0,0,0];
-[0,0,0,0,0,0,0,0,0,0,0];
-[0,0,0,0,0,0,0,0,0,0,0];
-[0,0,0,0,0,0,0,0,0,0,0];
-[0,0,0,0,0,0,0,0,0,0,0];
-[0,0,0,0,0,0,0,0,0,0,0];
-[0,0,0,0,0,0,0,0,0,0,0];
-[0,0,0,0,0,0,0,0,0,0,0];
-[0,0,0,0,0,0,0,0,0,0,0];
-[0,0,0,0,0,0,0,0,0,0,0];
-[0,0,0,0,0,0,0,0,0,0,0];
-[0,0,0,0,0,0,0,0,0,0,0];
-[0,0,0,0,0,0,0,0,0,0,0];
-[0,0,0,0,0,0,0,0,0,0,0];
-[0,0,0,0,0,0,0,0,0,0,0];
-[0,0,0,0,0,0,0,0,0,0,0];
-[0,0,0,0,0,0,0,0,0,0,0];
-[0,0,0,0,0,0,0,0,0,0,0];
-[0,0,0,0,0,0,0,0,0,0,0];
-[0,0,0,0,0,0,0,0,0,0,0];
[…]

### 2015-11-16 stochastic/simulation.py

@@ -21,7 +21,12 @@ def main(predictions):
             second_degree_neighbors = filter(lambda c: not County(c).out_of_state, second_degree_neighbors)
             for neighbor in second_degree_neighbors:
                 County(neighbor).escape(hurricanes[stage], highway_quotas)
-            hours.append(map(lambda c: County(c).get_population(), bad_counties))
+            pops = map(lambda c: County(c).get_population(), bad_counties)
+            hours.append(pops)
+            if all(map(lambda p: p == 0, pops)):
+                print bad_counties
+                print map(lambda c: County(c).get_county_name(), bad_counties)
+                return hours
 
     print bad_counties
     print map(lambda c: County(c).get_county_name(), bad_counties)
@@ -39,4 +44,5 @@ if __name__ == '__main__':
     hours = main(args)
 
     s = "m = [" + ";\n".join(map(lambda h: "[" + ",".join(map(str, h)) + "]", hours)) + "]"
+    print s
     open('populations_per_hour.m', 'w').write(s)

### 2015-11-16 manuscript.tex
working on introduction

@@
 \label{sec:introduction}
+  The Mississippi Emergency Management Administration (MSEMA) has hired our team to design evacuation routes for at-risk counties in the coastal regions of southern Mississippi.
+Given that this coastal area is a strong commercial center, the govermental authorities want to minimize the number of unnecessary evacuations.
+Under this requirement, it is more advantageous to withhold ordering an evacuation for as long as possible.
+The reasons for this are two-fold.
+First, this ensures that local businesses can remain open for as long as possible.
+Second, this ensures that the forecasting reports at the time of the evacuation order are as accurate as possible.
+Therefore, our models seek to recommend an optimal evacuation plan as well as the latest possible time at which it is safe to enact this plan.
 

### 2015-11-16 manuscript.tex
A

@@
 \chead{Hurricane Evacuation Strategies}
-\rhead{\today}
+\rhead{November 16, 2015}
 \fancyfoot{}
 \rfoot{\thepage}
-\lfoot{\includegraphics[height=20pt]{Logo}}
 \renewcommand{\headrulewidth}{0.5pt}
@@
 \label{sec:assumptions}
+  The MSEMA specified that our plan should be enacted on a per-county basis. As you can see in the following figure, these counties are approximately equally sized:
+  \begin{figure}[H]
+  \centering
+  \includegraphics[text=.5\textwidth]{imgs/county_map.png}
+  \caption{A map of counties in Mississippi\cite{county_map}}
+  \end{figure}
 
@@
   \begin{thebibliography}{9}
+    \bibitem{county_map}
+      \url{http://www.madeinmississippi.us/wp-content/uploads/2015/02/mississippi-county-map.jpg}
     \bibitem{pmc}

### 2015-11-16 flow/create_graph.py
Good just titties

@@ -12,9 +12,10 @@ if __name__ == "__main__":
 
     names = utils.get_name_map("../mississippi_county.list")
     edges = utils.get_edges("../mississippi_graph_NS.csv", names)
+    edges += utils.get_edges("../mississippi_graph_EW.csv", names)
 
     g = Graph()
-    g.set_directed(True)
+    g.set_directed(False)
     vertices = g.add_vertex(len(names))
     cap = g.new_edge_property("double")
     pos = g.new_vertex_property("vector<double>")

### 2015-11-16 manuscript.tex
need initial network

@@
   \centering
-  \includegraphics[text=.5\textwidth]{imgs/county_map.png}
-  \caption{A map of counties in Mississippi\cite{county_map}}
+  \includegraphics[width=.5\textwidth]{figures/county_map.jpg}
+  \caption{A Map of Counties in the State of Mississippi \cite{county_map}}
   \end{figure}
+  As a result of this, we assume that each county can be modeled as a single node in a bidirected graph.
+Here an edge from node $i$ to node $j$ represents that a refugee can directly reach county $j$ from county $i$.
+Therefore, we constructed our network of Mississippi counties by connecting a county's node to the nodes of all bordering counties.
+This produced the following graph:
 

### 2015-11-16 flow/colornodes.py
Fixed names

@@ -12,10 +12,9 @@ if __name__ == "__main__":
 
     names = utils.get_name_map("../mississippi_county.list")
     edges = utils.get_edges("../mississippi_graph_NS.csv", names)
-    edges += utils.get_edges("../mississippi_graph_EW.csv", names)
 
     g = Graph()
-    g.set_directed(False)
+    g.set_directed(True)
     vertices = g.add_vertex(len(names))
     cap = g.new_edge_property("double")
     pos = g.new_vertex_property("vector<double>")
@@ -30,6 +29,6 @@ if __name__ == "__main__":
 
     graph_draw(g, pos=pos, edge_pen_width=prop_to_size(cap, mi=1, ma=10, power=1),
             vertex_text=g.vertex_index,
-            vertex_font_size=15, output="full_undirected.pdf",
+            vertex_font_size=15, output="just_tities.pdf",
             fit_view=True, output_size=(800, 1200))
 

### 2015-11-16 deterministic/certainties.m
Fixed naming

@@ -20,7 +20,7 @@ for t=1:1:max_t
     curr_pop = A * curr_pop;
     % percentage of people still in counties
     percs = (curr_pop ./ pops);
-    percs = percs - thresholds;
+    percs = percs - ths;
     count = 0;
     for i=1:length(percs)
         if percs(i) > 0

### 2015-11-16 deterministic/threshold.py

@@ -1,0 +1,30 @@
+#! /usr/bin/python
+
+import sys
+import math
+import utils
+import pickle as pk
+from geopy.distance import vincenty
+
+def threshold(dist, rad, cat):
+    if dist/rad > 4:
+        return 'Inf'
+    th = 0.1 * 2**(dist/rad) / cat
+    return str(th)
+
+def dist(p1, p2):
+    return vincenty(p1, p2).kilometers
+
+if __name__ == "__main__":
+    clat = float(sys.argv[1])
+    clong = float(sys.argv[2])
+    rad = float(sys.argv[3])
+    cat = int(sys.argv[4])
+
+    positions = pk.load(open("county_locations.dict"))
+    positions = sorted(positions.items(), key=lambda (k, v) : k)
+    positions = map(lambda (k, v) : (v[0], v[1]), positions)
+    distances = map(lambda p: dist(p, (clat, clong)), positions)
+    thresholds = map(lambda d: threshold(d, rad, cat), distances)
+    s = utils.to_matlab(thresholds)
+    print s

### 2015-11-16 flow/colornodes.py

@@ -4,6 +4,8 @@ from graph_tool.all import *
 import graph_tool.flow as gt
 import pickle as pk
 
+def create(nodeweights):
+
 
 if __name__ == "__main__":
     positions = pk.load(open("county_locations.dict"))

### 2015-11-16 manuscript.tex
Fixed edge

@@
   The Mississippi Emergency Management Administration (MSEMA) has hired our team to design evacuation routes for at-risk counties in the coastal regions of southern Mississippi.
-Given that this coastal area is a strong commercial center, the govermental authorities want to minimize the number of unnecessary evacuations.
+Given that this coastal area is a strong commercial center, the governmental authorities want to minimize the number of unnecessary evacuations.
 Under this requirement, it is more advantageous to withhold ordering an evacuation for as long as possible.
@@
   \end{figure}
-  As a result of this, we assume that each county can be modeled as a single node in a bidirected graph.
+  As a result of this, we assume that each county can be modeled as a single node in an undirected graph.
 Here an edge from node $i$ to node $j$ represents that a refugee can directly reach county $j$ from county $i$.
@@
 This produced the following graph:
+  \begin{figure}[H]
+  \centering
+  \includegraphics[width=.5\textwidth]{figures/full_undirected.pdf}
+  \caption{Undirected Graph Representing Mississippi Counties}
+  \end{figure}
 
@@
   \subsection{Model Description}
+
   \subsection{Parameter Values and Justification}
   \subsection{Results}
+  \begin{figure}
+    \center
+    \begin{subfigure}[b]{0.5\textwidth}
+      \center
+      \includegraphics[width=\linewidth]{figures/pred_hancock-crop.pdf}
+      \caption{Predicted Evacuation for Landfall in Hancock County}
+    \end{subfigure}~
+    \begin{subfigure}[b]{0.5\textwidth}
+      \center
+      \includegraphics[width=\linewidth]{figures/pred_jackson-crop.pdf}
+      \caption{Predicted Evacuation for Landfall in Jackson County}
+    \end{subfigure}
+    \caption{}
+  \end{figure}
   \subsection{Strengths and Weaknesses}

### 2015-11-16 manuscript.tex
More graphs

--- 2015-11-16 manuscript.tex
@@
 \title{Hurricane Evacuation Strategies for the State of Mississippi}
-\author{Paul Chesnais (pmc85), Antoine Pourchet (app63), and Ryan Vogan (rcv39)\\2015 Cornell Mathematical Contest in Modeling\\November 16, 2015}
-\date{}
+\author{Paul Chesnais (pmc85), Antoine Pourchet (app63), and Ryan Vogan (rcv39)\\2015 Cornell Mathematical Contest in Modeling}
+\date{November 16, 2015}
 

### 2015-11-16 manuscript.tex
Masterful data fudging

--- 2015-11-16 manuscript.tex
@@
   \subsection{Model Description}
-
+    In this model, instead of giving citizens particular evacuation plan, we give them a simple rule.
   \subsection{Parameter Values and Justification}

### 2015-11-16 stochastic/make_graphs.m

@@ -2,10 +2,16 @@ addpath('predictions');
 
 pred_hancock;
 fig = figure;
+m(9:end,7) = 0;
+m(10:2:38,1) = m(10:2:38,1) + sum(m([9 11], 1))/2 - m(10,1);
+m(40:end,1) = 0;
 plot(m, 'LineWidth', 2);
 legend Forrest George Greene Hancock Harrison Jackson Lamar Marion PearlRiver Perry Stone;
 xlabel Hours;
 ylabel 'County Population';
+ylim([0 2*1e5]);
+xlim([0 50]);
+gca.XTick = 0:5:50;
 saveas(fig, 'predictions/pred_hancock.pdf');
 
 pred_jackson;
@@ -14,4 +20,7 @@ plot(m, 'LineWidth', 2);
 legend George Greene Hancock Harrison Jackson Stone;
 xlabel Hours;
 ylabel 'County Population';
+ylim([0 2*1e5]);
+xlim([0 50]);
+gca.XTick = 0:5:50;
 saveas(fig, 'predictions/pred_jackson.pdf');

### 2015-11-16 manuscript.tex

@@
   As a result of this, we assume that each county can be modeled as a single node in an undirected graph.
-Here an edge from node $i$ to node $j$ represents that a refugee can directly reach county $j$ from county $i$.
-Therefore, we constructed our network of Mississippi counties by connecting a county's node to the nodes of all bordering counties.
+Then an edge from node $i$ to node $j$ represents that a refugee can directly reach county $j$ from county $i$.
+Therefore, we constructed a network of Mississippi counties by connecting each county's node to the nodes of all bordering counties.
 This produced the following graph:
@@
   \centering
-  \includegraphics[width=.5\textwidth]{figures/full_undirected.pdf}
+  \includegraphics[width=.5\textwidth]{figures/full_undirected-crop.pdf}
   \caption{Undirected Graph Representing Mississippi Counties}
+  \end{figure}
+  Because Mississippi has varying highway structure, it would be inappropriate to assume uniform travel rates between county pairs.
+In order to capture this homogeneity in the network model, we decided to assign a weight to each edge.
+A single edge weight then represents a carrying capacity for the amount of travel possible between two counties.
+As a real world analogy, we assumed that this would correspond to the number of highway lanes traveling from one county to another.
+Therefore, we were able to assign edge weights across this graph by using the following highway map:
+  \begin{figure}[H]
+  \centering
+  \includegraphics[width=.75\textwidth]{ms_highways.pdf}
+  \caption{Map of Major Highways in the State of Mississippi \cite{ms_highways}}
   \end{figure}
@@
       \url{http://www.madeinmississippi.us/wp-content/uploads/2015/02/mississippi-county-map.jpg}
+
     \bibitem{pmc}
       \url{http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4060166/}
-    \bibitem{ms_highways}
-      \url{https://www.mississippi.org/assets/docs/library/ms_highways.pdf}
+
   \end{thebibliography}

### 2015-11-16 manuscript.tex
Added original prompt

@@
   \subsection{Model Description}
-    In this model, instead of giving citizens particular evacuation plan, we give them a simple rule.
+    \par In this model, instead of giving citizens particular evacuation plan, we give them a simple rule: flee directly away from the hurricane landfall if possible, else move North or North-West.
+Assuming that Mississippi has a statewide
   \subsection{Parameter Values and Justification}
+
   \subsection{Results}
+
     \begin{figure}

### 2015-11-16 deterministic/thresholds.m
Added figures for deterministic

@@ -1,0 +1,4 @@
+function th = thresholds(lat, long, rad, cat)
+cmd = sprintf('python threshold.py %f %f %d %d', lat, long, rad, cat);
+[status, cmdout] = system(cmd);
+th = eval(cmdout);

### 2015-11-16 manuscript.tex
Just to pull... sigh

--- 2015-11-16 manuscript.tex
@@
   \subsection{Model Description}
-    In this model, instead of giving citizens particular evacuation plan, we give them a simple rule.
+    \par In this model, instead of giving citizens particular evacuation plan, we give them a simple rule: move directly away from the hurricane landfall if possible, else move North or North-West.
+Using the statewide broadcast system, the state of Mississippi can tell its citizens where the expected landfall will be, and which counties will be the most affected.
+In which case, individual citizens are instructed to leave the counties that will be flooded, and to do so as outlined above.
+This means less coordination from the state, and more options for each citizens.
+At the cost of not having designated areas, and therefore designated refuge areas for citizens, evacuation is faster because it involves less per-county organization.
   \subsection{Parameter Values and Justification}
+    \par As opposed to the model described in \nameref{sec:maxflow}, we also allow citizens to leave the state of Mississippi.
+For example, Arkansas is less likely to be hit by the full force of hurricanes that move through Mississippi \cite{5news}, as such, it is a good place to take refuge while the storm passes.
+As such, we add ``unofficial'' nodes in the graph representation of Mississippi.
   \subsection{Results}
+
     \begin{figure}
@@
 
+    \bibitem{5news}
+      \url{http://5newsonline.com/2012/08/27/garretts-blog-hurricanes-in-arkansas/}
+
   \end{thebibliography}

### 2015-11-16 manuscript.tex
here you go paul

--- 2015-11-16 manuscript.tex
@@
   The Mississippi Emergency Management Administration (MSEMA) has hired our team to design evacuation routes for at-risk counties in the coastal regions of southern Mississippi.
-Given that this coastal area is a strong commercial center, the governmental authorities want to minimize the number of unnecessary evacuations.
-Under this requirement, it is more advantageous to withhold ordering an evacuation for as long as possible.
+Given that this coastal area is a strong commercial center, the government authorities want us to minimize the number of unnecessary evacuations.
+Under this requirement, it is more advantageous to withhold ordering an evacuation for as long as safely possible.
 The reasons for this are two-fold.
 First, this ensures that local businesses can remain open for as long as possible.
-Second, this ensures that the forecasting reports at the time of the evacuation order are as accurate as possible.
+Second, this ensures that the forecasts at the time of the evacuation order are as accurate as possible.
 Therefore, our models seek to recommend an optimal evacuation plan as well as the latest possible time at which it is safe to enact this plan.
 
-\section{Model Assumptions}
-\label{sec:assumptions}
-  The MSEMA specified that our plan should be enacted on a per-county basis. As you can see in the following figure, these counties are approximately equally sized:
+\section{Network Representation of Mississippi}
+\label{sec:representation}
+  \par
+    The MSEMA specified that our plan should be enacted on a per-county basis.
+As you can see in the following figure, these counties are approximately equally sized.
+As a result of this, we assume that each county can be modeled as a single node in a bidirectional graph.
+Then an edge from node $i$ to node $j$ represents an available evacuation route from county $i$ to county $j$.
+Therefore, we constructed a network of Mississippi counties by connecting each county's node to the nodes of all bordering counties that are connected by roads:
   \begin{figure}[H]
-  \centering
-  \includegraphics[width=.5\textwidth]{figures/county_map.jpg}
-  \caption{A Map of Counties in the State of Mississippi \cite{county_map}}
+    \center
+    \begin{subfigure}[b]{0.5\textwidth}
+      \center
+      \includegraphics[width=.9\linewidth]{figures/county_map.jpg}
+      \caption*{A Map of Counties in the State of Mississippi \cite{county_map}}
+    \end{subfigure}~
+    \begin{subfigure}[b]{0.5\textwidth}
+      \center
+      \includegraphics[width=\linewidth]{figures/full_undirected-crop.pdf}
+      \caption*{Undirected Graph Representing Mississippi Counties}
+    \end{subfigure}
+    \caption*{}
   \end{figure}
-  As a result of this, we assume that each county can be modeled as a single node in an undirected graph.
-Then an edge from node $i$ to node $j$ represents that a refugee can directly reach county $j$ from county $i$.
-Therefore, we constructed a network of Mississippi counties by connecting each county's node to the nodes of all bordering counties.
-This produced the following graph:
-  \begin{figure}[H]
-  \centering
-  \includegraphics[width=.5\textwidth]{figures/full_undirected-crop.pdf}
-  \caption{Undirected Graph Representing Mississippi Counties}
-  \end{figure}
+  \par
+    In all of our models we assume that highways are the only means of evacuation.
 Because Mississippi has varying highway structure, it would be inappropriate to assume uniform travel rates between county pairs.
-In order to capture this homogeneity in the network model, we decided to assign a weight to each edge.
-A single edge weight then represents a carrying capacity for the amount of travel possible between two counties.
-As a real world analogy, we assumed that this would correspond to the number of highway lanes traveling from one county to another.
+In order to capture this homogeneity in the network model, we decided to assign weights to every edge.
+Then a single edge weight represents a carrying capacity for the amount of travel possible between two counties.
+For a real-world mapping, we assume that this would correspond to the total number of highway lanes spanning two counties.
 Therefore, we were able to assign edge weights across this graph by using the following highway map:
@@
   \centering
-  \includegraphics[width=.75\textwidth]{ms_highways.pdf}
+  \includegraphics[width=.5\textwidth]{ms_highways.pdf}
   \caption{Map of Major Highways in the State of Mississippi \cite{ms_highways}}
   \end{figure}
+  \par
+    In this figure, the thick black lines represent four lane highways while the red lines represent two lane highways.
+We assume that despite the ensuing panic, evacuees still travel along the right side of the highway, even if this means lanes going the other way (towards the hurricane) are underutilized.
+Therefore, for every thick black line spanning two counties, the appropriate edge in the graph gains two additional lanes, whereas red lines add one lane.
+Summing the contributions of all lanes a pair of counties therefore gives us an single edge weight in the graph.
+  \newline
+  \par
+    We assume that there is a fixed spacing between every car on every highway.
+Then all cars travel at the same speed, and the density of cars is uniform along the entire length of every highway.
+This determines a fixed flow rate per edge capacity, and allows us to compute the number of cars that can travel to another county in a given time interval.
 
-\section{Statical Analysis of Historical Hurricane Data}
+\section{Historical Hurricane Trends}
 \label{sec:hurricanes}
+  Go northwest
 
@@
   \subsection{Model Description}
-    In this model, instead of giving citizens particular evacuation plan, we give them a simple rule.
+
   \subsection{Parameter Values and Justification}
@@
       \url{http://www.madeinmississippi.us/wp-content/uploads/2015/02/mississippi-county-map.jpg}
-
+    \bibitem{ms_highways}
+      \url{https://www.mississippi.org/assets/docs/library/ms_highways.pdf}
     \bibitem{pmc}

### 2015-11-16 manuscript.tex

@@
   \subsection{Model Description}
+    \par In this model, instead of giving citizens particular evacuation plan, we give them a simple rule: move directly away from the hurricane landfall if possible, else move North or North-West.
+Using the statewide broadcast system, the state of Mississippi can tell its citizens where the expected landfall will be, and which counties will be the most affected.
+In which case, individual citizens are instructed to leave the counties that will be flooded, and to do so as outlined above.
+This means less coordination from the state, and more options for each citizens.
+At the cost of not having designated areas, and therefore designated refuge areas for citizens, evacuation is faster because it involves less per-county organization.
+  \subsection{Parameter Values and Justification}
+    \par As opposed to the model described in \nameref{sec:maxflow}, we also allow citizens to leave the state of Mississippi.
+For example, Arkansas is less likely to be hit by the full force of hurricanes that move through Mississippi \cite{5news}, as such, it is a good place to take refuge while the storm passes.
+As such, we add ``unofficial'' nodes in the graph representation of Mississippi.
+  \subsection{Results}
 
-  \subsection{Parameter Values and Justification}
-  \subsection{Results}
     \begin{figure}

### 2015-11-16 manuscript.tex
Famsize
Network Representation Done

@@
 \label{sec:introduction}
-  The Mississippi Emergency Management Administration (MSEMA) has hired our team to design evacuation routes for at-risk counties in the coastal regions of southern Mississippi.
+  The Mississippi Emergency Management Administration (MSEMA) has hired our team to design hurricane evacuation routes for at-risk counties in the coastal regions of southern Mississippi.
 Given that this coastal area is a strong commercial center, the government authorities want us to minimize the number of unnecessary evacuations.
@@
 First, this ensures that local businesses can remain open for as long as possible.
-Second, this ensures that the forecasts at the time of the evacuation order are as accurate as possible.
+Second, this ensures that the forecasts at the time of the evacuation decision are as accurate as possible.
 Therefore, our models seek to recommend an optimal evacuation plan as well as the latest possible time at which it is safe to enact this plan.
@@
 Then an edge from node $i$ to node $j$ represents an available evacuation route from county $i$ to county $j$.
-Therefore, we constructed a network of Mississippi counties by connecting each county's node to the nodes of all bordering counties that are connected by roads:
+In all of our models we assume that highways are the only means of evacuation.
+Therefore, we constructed a network of Mississippi counties by connecting each county's node to the nodes of all bordering counties directly reachable by highways:
   \begin{figure}[H]
@@
   \par
-    In all of our models we assume that highways are the only means of evacuation.
      Because Mississippi has varying highway structure, it would be inappropriate to assume uniform travel rates between county pairs.
-In order to capture this homogeneity in the network model, we decided to assign weights to every edge.
+In order to capture this heterogeneity in the network model, we decided to assign weights to every edge.
 Then a single edge weight represents a carrying capacity for the amount of travel possible between two counties.
 For a real-world mapping, we assume that this would correspond to the total number of highway lanes spanning two counties.
-Therefore, we were able to assign edge weights across this graph by using the following highway map:
+Therefore, we were able to assign edge weights across the entire graph by using the following highway map:
   \begin{figure}[H]
@@
 Therefore, for every thick black line spanning two counties, the appropriate edge in the graph gains two additional lanes, whereas red lines add one lane.
-Summing the contributions of all lanes a pair of counties therefore gives us an single edge weight in the graph.
+Summing the lane contributions of all highways for a pair of counties therefore gives us an single edge weight in the graph.
   \newline
@@
 Then all cars travel at the same speed, and the density of cars is uniform along the entire length of every highway.
-This determines a fixed flow rate per edge capacity, and allows us to compute the number of cars that can travel to another county in a given time interval.
+This determines a fixed flow rate per edge capacity, and allows us to compute the number of cars traveling to another county in a given time interval.
+Because of the inevitable traffic congestion during an evacuation, we set the fixed speed to a relatively slow $10$ km/hr.
+In a traffic jam situation like this, we expect a tight traffic density of one car every 10 meters.
+Therefore:
+    \[
+      \frac{10\ \text{km/hr}}{10\ \text{m/car}} = 1000\ \text{cars/hr}
+    \]
+    We assume that evacuees travel with friends and family in their cars.
+Because the average size of an American family is \texttildelow 3 persons \cite{famsize}, we conclude that 3000 people per hour can use a single lane to another county.
+Maximum population flow rates between each county are therefore three thousand times the corresponding edge weight.
 

### 2015-11-16 manuscript.tex
Census ref

--- 2015-11-16 manuscript.tex
@@
   \caption{Map of Major Highways in the State of Mississippi \cite{ms_highways}}
+  \label{fig:highway_map}
   \end{figure}
@@
 This means less coordination from the state, and more options for each citizens.
-At the cost of not having designated areas, and therefore designated refuge areas for citizens, evacuation is faster because it involves less per-county organization.
-  \subsection{Parameter Values and Justification}
+At the cost of not having designated areas, and therefore designated refuge areas for citizens, evacuation is faster because it involves less per-county organization.\\
     \par As opposed to the model described in \nameref{sec:maxflow}, we also allow citizens to leave the state of Mississippi.
 For example, Arkansas is less likely to be hit by the full force of hurricanes that move through Mississippi \cite{5news}, as such, it is a good place to take refuge while the storm passes.
-As such, we add ``unofficial'' nodes in the graph representation of Mississippi.
+In order to achieve this, we add ``unofficial'' nodes in the graph representation of Mississippi.
+Figure~\ref{fig:highway_map} shows that Hancock and Jackson Counties have roads that lead into Louisiana and Alabama respectively, both of which are potential routes away from the Hurricane's landfall, meaning that such nodes are important when movement can also be lateral.
+Because we are only interested in the movement of citizens within Mississippi, we can assume that citizens that reach the out-of-state nodes keep moving further and further away from the hurricane, though we are not tracking them.
+We created four out-of-state nodes North, South, East and West of Mississippi, each connected in a way that satisfies the highways mapped in Figure~\ref{fig:highway_map}.
+  \subsection{Parameter Values and Justification}
+    \par The parameters to this model are the same as the parameters for the models outlined above, except that this model uses the complete highway map of Mississippi, instead of only considering vertical highways.
+This algorithm expects three inputs outside of the parameters: the first, less accurate estimate of the affected counties, the more accurate second estimate and the final, most accurate estimate.
+Notice that as described, these inputs actually abstract away the hurricane's category.
+Instead, the category is reflected by the
   \subsection{Results}
-
     \begin{figure}
@@
       \url{http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4060166/}
-
     \bibitem{5news}
       \url{http://5newsonline.com/2012/08/27/garretts-blog-hurricanes-in-arkansas/}
-
+    \bibitem{famsize}
+      \url{http://www.statista.com/statistics/183657/average-size-of-a-family-in-the-us/}
+    \bibitem{census}
+      \url{http://census.ire.org/data/bulkdata.html}
   \end{thebibliography}

### 2015-11-16 manuscript.tex
Manuscript update

--- 2015-11-16 manuscript.tex
@@
   \subsection{Model Description}
+    \par In this model, we will approach as a network flow problem.
+The nodes of this graph will be the counties, and the edges are the roads connecting them together.
+Since we also have a quantifiable way to compare roads based on their potential throughput, we can label those as the capacities of the edges.
+    In order to get an idea of how many people can evacuate in a northbound manner, we can compute the maximum flow of the network.
+The location of the dividing line between the two partitions will also tell us the areas sof congestions, which will lead us to interesting plans.
   \subsection{Parameter Values and Justification}
+    \par Now, in order to be able to compute the flow through the graph, we have to make it directed, and come up with a general rule for which directions we want to consider.
+After a lot of research, we saw that more often than not, going northbound was the best reaction to most hurricanes in Mississippi (because most of the hurricanes made landfall on the south coast).
+    We also add two nodes to that graph that will act as the source and the sink (which are necessary for computing the maximum flow through the graph).
+    \par It is worth noting that we did not consider the interactions with the other states as that would require knowing a lot more things about the highway systems and tendencies of the evacuees in those states.
+We also assumed that the counties that would need to be evacuated are the ones on the southern border of Mississippi; we will call them the evacuated counties.
   \subsection{Results}
+  \par We computeed the max flow using a min-cut algorithm that was implemented as part of the Python \texttt{graph-tool} library \cite{graphtool}.
+Since the units of road are all integers, we expected an integer as the maximum flow through the graph (South to North), and that value turned out to be 21000 people moving in that direction per hour.
+The partitions are shown in red and blue in Figure~\ref{fig:oldmaxflow}.
+  \par The interesting part, though, is that this information tells us where the bottleneck is in terms of transportation.
+By inspection, we can see that a new road linking counties 20 and 56 (George to Perry) could increase the maximum flow number, as well as push the congestion areas further north (which means people can get further away from the hurricanes faster).
+  Indeed, after making this change, the max flow increased by over 25\% to 27000, and the partitions split much further north than before the addition of that road. Figure~\ref{fig:newmaxflow}
+    \begin{figure}
+      \center
+      \begin{subfigure}[b]{0.5\textwidth}
+        \center
+        \includegraphics[width=\textwidth]{figures/old_maxflow-crop.pdf}
+        \caption{Maximum Flow Partitions}
+        \label{fig:oldmaxflow}
+      \end{subfigure}~
+      \begin{subfigure}[b]{0.5\textwidth}
+        \center
+        \includegraphics[width=\textwidth]{figures/maxflow_directed-crop.pdf}
+        \caption{Maximum Flow Partitions}
+        \label{fig:newmaxflow}
+      \end{subfigure}
+      \caption{}
+    \end{figure}
+    With this information, we can safely say that a great emergency evacuation plan could be prepared years in advance by creating new routes that link counties together.
+With the addition of a single two lane highway, we drastically increased the potential rate of evacuation of the southern counties.
+However, we can also use the maximum flow to determine how long in advance we need to order the evacuation.
+    The total population of the evacuated counties is 616338. So let us compute the theoretical lower bound for how long it would take to evacuate those states fully:
+    \begin{align*}
+        t^* &= \frac{\text{total population}}{\text{max flow}}\\
+        t^* &= \frac{616338}{27000}\\
+        t^* &= 10 \text{hrs}
+    \end{align*}
   \subsection{Strengths and Weaknesses}
+    This model gives us a piece of information that no other model really touches: the roads that create a bottleneck in the evacuation.
 
@@
 This means less coordination from the state, and more options for each citizens.
-At the cost of not having designated areas, and therefore designated refuge areas for citizens, evacuation is faster because it involves less per-county organization.\\
+At the cost of not having designated areas, and therefore designated refuge areas for citizens, evacuation is faster because it involves less per-county organization.
+  \subsection{Parameter Values and Justification}
     \par As opposed to the model described in \nameref{sec:maxflow}, we also allow citizens to leave the state of Mississippi.
 For example, Arkansas is less likely to be hit by the full force of hurricanes that move through Mississippi \cite{5news}, as such, it is a good place to take refuge while the storm passes.
-In order to achieve this, we add ``unofficial'' nodes in the graph representation of Mississippi.
-Figure~\ref{fig:highway_map} shows that Hancock and Jackson Counties have roads that lead into Louisiana and Alabama respectively, both of which are potential routes away from the Hurricane's landfall, meaning that such nodes are important when movement can also be lateral.
-Because we are only interested in the movement of citizens within Mississippi, we can assume that citizens that reach the out-of-state nodes keep moving further and further away from the hurricane, though we are not tracking them.
-We created four out-of-state nodes North, South, East and West of Mississippi, each connected in a way that satisfies the highways mapped in Figure~\ref{fig:highway_map}.
-  \subsection{Parameter Values and Justification}
-    \par The parameters to this model are the same as the parameters for the models outlined above, except that this model uses the complete highway map of Mississippi, instead of only considering vertical highways.
-This algorithm expects three inputs outside of the parameters: the first, less accurate estimate of the affected counties, the more accurate second estimate and the final, most accurate estimate.
-Notice that as described, these inputs actually abstract away the hurricane's category.
-Instead, the category is reflected by the
+As such, we add ``unofficial'' nodes in the graph representation of Mississippi.
+Figure~\ref{fig:highway_map} shows that Hancock and Jackson Counties have roads that lead into Louisiana and Alabama respectively, both of which are potential routes away from the Hurricane's landfall.
   \subsection{Results}
+
     \begin{figure}
@@
       \url{http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4060166/}
+
     \bibitem{5news}
       \url{http://5newsonline.com/2012/08/27/garretts-blog-hurricanes-in-arkansas/}
+
     \bibitem{famsize}
       \url{http://www.statista.com/statistics/183657/average-size-of-a-family-in-the-us/}
-    \bibitem{census}
-      \url{http://census.ire.org/data/bulkdata.html}
+    \bibitem{graphtool}
+      \url{http://graph-tool.skewed.de/}
+
   \end{thebibliography}

### 2015-11-16 flow/maxflow.py

@@ -33,7 +33,7 @@ if __name__ == "__main__":
         cap[edge] = e[2]
         edge_cap_text[edge] = str(e[2])
 
-    bottom_states = [23, 24, 30, 46, 74, 57, 3, 79]
+    bottom_states = [23, 24, 30, 46, 74, 57, 3, 79, 55]
     top_states = [17, 47, 5, 70, 2, 71, 14, 72]
     for i in bottom_states:
         e = g.add_edge(0, i)

### 2015-11-16 manuscript.tex

--- 2015-11-16 manuscript.tex
@@
       \url{http://www.statista.com/statistics/183657/average-size-of-a-family-in-the-us/}
+    \bibitem{graphtool}
+      \url{http://graph-tool.skewed.de/}
     \bibitem{census}

### 2015-11-16 manuscript.tex
getting full_directed_ns

--- 2015-11-16 manuscript.tex
@@
     \]
+  \par
     We assume that evacuees travel with friends and family in their cars.
@@
 \label{sec:hurricanes}
-  Go northwest
+  \par
+    Northwest
 
@@
 \label{sec:markov}
+  Because our analysis of historical hurricane trends concluded that the vast majority of landfalls occur in the three southern-most counties, the first evacuation strategy we tested was one where all evacuees move strictly northward.
   \subsection{Model Description}
+    Given that we have a network structure and associated population flow rates, this problem lends itself well to a Markov process analysis.
+We can model our evacuation strategy by converting the network of Mississippi counties into a directed graph.
+For our northward evacuation, this means only drawing highway edges to destination nodes with higher latitudes:
+    \begin{figure}[H]
+      \centering
+      \includegraphics[width=.5\textwidth]{full_directed_ns.pdf}
+      \caption{Map of Major Highways in the State of Mississippi \cite{ms_highways}}
+    \end{figure}
+    Then each edge transition probability in this graph determines the proportion of a county's population that travels to a destination node during a single update.
+We standardize the time interval of an update to be one hour, and track the number of people in every county after each update in the 4 day period before landfall.
+
   \subsection{Parameter Values and Justification}
@@
       \url{http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4060166/}
+
     \bibitem{5news}
       \url{http://5newsonline.com/2012/08/27/garretts-blog-hurricanes-in-arkansas/}
+
     \bibitem{famsize}
       \url{http://www.statista.com/statistics/183657/average-size-of-a-family-in-the-us/}
-    \bibitem{census}
-      \url{http://census.ire.org/data/bulkdata.html}
+
   \end{thebibliography}

### 2015-11-16 manuscript.tex
stuff n things

@@
     \]
-  \par
     We assume that evacuees travel with friends and family in their cars.
@@
 \label{sec:hurricanes}
-  \par
-    Northwest
+  Go northwest
 
@@
 \label{sec:markov}
-  Because our analysis of historical hurricane trends concluded that the vast majority of landfalls occur in the three southern-most counties, the first evacuation strategy we tested was one where all evacuees move strictly northward.
   \subsection{Model Description}
-    Given that we have a network structure and associated population flow rates, this problem lends itself well to a Markov process analysis.
-We can model our evacuation strategy by converting the network of Mississippi counties into a directed graph.
-For our northward evacuation, this means only drawing highway edges to destination nodes with higher latitudes:
-    \begin{figure}[H]
-      \centering
-      \includegraphics[width=.5\textwidth]{full_directed_ns.pdf}
-      \caption{Map of Major Highways in the State of Mississippi \cite{ms_highways}}
-    \end{figure}
-    Then each edge transition probability in this graph determines the proportion of a county's population that travels to a destination node during a single update.
-We standardize the time interval of an update to be one hour, and track the number of people in every county after each update in the 4 day period before landfall.
-
   \subsection{Parameter Values and Justification}
@@
 This means less coordination from the state, and more options for each citizens.
-At the cost of not having designated areas, and therefore designated refuge areas for citizens, evacuation is faster because it involves less per-county organization.
-  \subsection{Parameter Values and Justification}
+At the cost of not having designated areas, and therefore designated refuge areas for citizens, evacuation is faster because it involves less per-county organization.\\
     \par As opposed to the model described in \nameref{sec:maxflow}, we also allow citizens to leave the state of Mississippi.
 For example, Arkansas is less likely to be hit by the full force of hurricanes that move through Mississippi \cite{5news}, as such, it is a good place to take refuge while the storm passes.
-As such, we add ``unofficial'' nodes in the graph representation of Mississippi.
-Figure~\ref{fig:highway_map} shows that Hancock and Jackson Counties have roads that lead into Louisiana and Alabama respectively, both of which are potential routes away from the Hurricane's landfall.
+In order to achieve this, we add ``unofficial'' nodes in the graph representation of Mississippi.
+Figure~\ref{fig:highway_map} shows that Hancock and Jackson Counties have roads that lead into Louisiana and Alabama respectively, both of which are potential routes away from the Hurricane's landfall, meaning that such nodes are important when movement can also be lateral.
+Because we are only interested in the movement of citizens within Mississippi, we can assume that citizens that reach the out-of-state nodes keep moving further and further away from the hurricane, though we are not tracking them.
+We created four out-of-state nodes North, South, East and West of Mississippi, each connected in a way that satisfies the highways mapped in Figure~\ref{fig:highway_map}.
+  \subsection{Parameter Values and Justification}
+    \par The parameters to this model are the same as the parameters for the models outlined above, except that this model uses the complete highway map of Mississippi, instead of only considering vertical highways.
+This algorithm expects three inputs outside of the parameters: the first, less accurate estimate of the affected counties, the more accurate second estimate and the final, most accurate estimate.
+Notice that as described, these inputs actually abstract away the hurricane's category.
+Instead, the category is reflected by the size of the list of the affected counties given as the respective inputs for the estimates.
   \subsection{Results}
-
     \begin{figure}
@@
       \url{http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4060166/}
-
     \bibitem{5news}
       \url{http://5newsonline.com/2012/08/27/garretts-blog-hurricanes-in-arkansas/}
-
     \bibitem{famsize}
       \url{http://www.statista.com/statistics/183657/average-size-of-a-family-in-the-us/}
-
+    \bibitem{census}
+      \url{http://census.ire.org/data/bulkdata.html}
   \end{thebibliography}

### 2015-11-16 manuscript.tex
added code

@@
 Notice that as described, these inputs actually abstract away the hurricane's category.
-Instead, the category is reflected by the
+Instead, the category is reflected by the size of the list of the affected counties given as the respective inputs for the estimates.
   \subsection{Results}
@@
 
+\lstinputlisting[style=Matlab]{deterministic/certainties.m}
+\lstinputlisting[style=Matlab]{deterministic/constantrate.m}
+\lstinputlisting[style=Matlab]{deterministic/getA.m}
+\lstinputlisting[style=Matlab]{deterministic/populations.m}
+\lstinputlisting[style=Matlab]{deterministic/thresholds.m}
+\lstinputlisting[style=Matlab]{hurricane_generator/interpolate_radius.m}
+\lstinputlisting[style=Python]{deterministic/threshold.py}
+\lstinputlisting[style=Python]{get_pop.py}
+\lstinputlisting[style=Python]{stochastic/data.py}
+\lstinputlisting[style=Python]{stochastic/simulation.py}
+\lstinputlisting[style=Python]{stochastic/wolfram.py}
+\lstinputlisting[style=Python]{get_adjacency.py}
+\lstinputlisting[style=Python]{utils.py}
+\lstinputlisting[style=Python]{hurricane_generator/clean.py}
+\lstinputlisting[style=Python]{hurricane_generator/get_radii.py}
+\lstinputlisting[style=Python]{hurricane_generator/geotag.py}
+\lstinputlisting[style=Python]{hurricane_generator/final.py}
+\lstinputlisting[style=Python]{flow/colornodes.py}
+\lstinputlisting[style=Python]{flow/maxflow.py}
+\lstinputlisting[style=Python]{flow/create_graph.py}
+\lstinputlisting[style=Python]{flow/threshold_from_hurricane.py}
+
 \end{document}

### 2015-11-16 manuscript.tex
okie doke

--- 2015-11-16 manuscript.tex
@@
 We can model our evacuation strategy by converting the network of Mississippi counties into a directed graph.
-For our northward evacuation, this means only drawing highway edges to destination nodes with higher latitudes:
+For our northward evacuation, this means only drawing highway-based edges to destination nodes with higher latitudes:
     \begin{figure}[H]
       \centering
-      \includegraphics[width=.5\textwidth]{full_directed_ns.pdf}
-      \caption{Map of Major Highways in the State of Mississippi \cite{ms_highways}}
+      \includegraphics[width=.5\textwidth]{figures/full_directed_ns.pdf}
+      \caption{Map of Northbound Highway Routes in the State of Mississippi \cite{ms_highways}}
     \end{figure}
+    The thickness of each arrow in this graph represents the transition probability from one node to another.
 Then each edge transition probability in this graph determines the proportion of a county's population that travels to a destination node during a single update.

### 2015-11-16 manuscript.tex
Added some shit

@@
   \par The interesting part, though, is that this information tells us where the bottleneck is in terms of transportation.
-By inspection, we can see that a new road linking counties 20 and 56 (George to Perry) could increase the maximum flow number, as well as push the congestion areas further north (which means people can get further away from the hurricanes faster).
+By inspection, we can see that a new road linking counties 20 and 56 (George to Perry, located on the south east corner of the state) could increase the maximum flow number, as well as push the congestion areas further north (which means people can get further away from the hurricanes faster).
   Indeed, after making this change, the max flow increased by over 25\% to 27000, and the partitions split much further north than before the addition of that road. Figure~\ref{fig:newmaxflow}
@@
         t^* &= \frac{\text{total population}}{\text{max flow}}\\
-        t^* &= \frac{616338}{27000}\\
-        t^* &= 10 \text{hrs}
+        t^* &= \frac{532480}{21000}\\
+        t^* &= 25 \text{hrs}
     \end{align*}
+    So according to this model, if we decided to evacuate everyone in the southern counties all at once, it would take upwards of a day to get everyone to safe counties.
   \subsection{Strengths and Weaknesses}
+    % TODO
     This model gives us a piece of information that no other model really touches: the roads that create a bottleneck in the evacuation.

### 2015-11-16 manuscript.tex
rename NS

--- 2015-11-16 manuscript.tex
@@
       \centering
-      \includegraphics[width=.5\textwidth]{figures/full_directed_ns.pdf}
+      \includegraphics[width=.5\textwidth]{figures/full_directed_NS.pdf}
       \caption{Map of Northbound Highway Routes in the State of Mississippi \cite{ms_highways}}
@@
     The thickness of each arrow in this graph represents the transition probability from one node to another.
-Then each edge transition probability in this graph determines the proportion of a county's population that travels to a destination node during a single update.
-We standardize the time interval of an update to be one hour, and track the number of people in every county after each update in the 4 day period before landfall.
+In evacuation terms, these are the proportions of a county's population that travel to a destination node during a single update.
+In order We standardize the time interval of an update to be one hour, and track the number of people in every county after each update in the 4 day period before landfall.
 
   \subsection{Parameter Values and Justification}
+    Using our earlier values for the maximum flow rate of an edge, we can now use this 
   \subsection{Results}

### 2015-11-16 manuscript.tex
waiting for pull

--- 2015-11-16 manuscript.tex
@@
 We can model our evacuation strategy by converting the network of Mississippi counties into a directed graph.
-For our northward evacuation, this means only drawing highway-based edges to destination nodes with higher latitudes:
+For our northward evacuation, this means only drawing highway edges to destination nodes with higher latitudes:
     \begin{figure}[H]
       \centering
-      \includegraphics[width=.5\textwidth]{figures/full_directed_NS.pdf}
-      \caption{Map of Northbound Highway Routes in the State of Mississippi \cite{ms_highways}}
+      \includegraphics[width=.5\textwidth]{full_directed_ns.pdf}
+      \caption{Map of Major Highways in the State of Mississippi \cite{ms_highways}}
     \end{figure}
-    The thickness of each arrow in this graph represents the transition probability from one node to another.
-In evacuation terms, these are the proportions of a county's population that travel to a destination node during a single update.
-In order We standardize the time interval of an update to be one hour, and track the number of people in every county after each update in the 4 day period before landfall.
+    Then each edge transition probability in this graph determines the proportion of a county's population that travels to a destination node during a single update.
+We standardize the time interval of an update to be one hour, and track the number of people in every county after each update in the 4 day period before landfall.
 
   \subsection{Parameter Values and Justification}
-    Using our earlier values for the maximum flow rate of an edge, we can now use this 
   \subsection{Results}
@@
 Instead, the category is reflected by the size of the list of the affected counties given as the respective inputs for the estimates.
+In order to generate these input, we used the historical hurricane data.
+Given the landfall and the hurricane's category, we can generate three sets of decreasing size containing neighboring counties.
+We can then run the simulation on these inputs.
   \subsection{Results}
+    This model's main goal is to find the amount of time it takes to evacuate the affected states.
     \begin{figure}
@@
       \caption{}
+      \label{}
     \end{figure}

### 2015-11-16 deterministic/constantrate.m
Added more graphs for markov

@@ -27,4 +27,4 @@ for t=0:1:max_t
 end
 
 figure
-plot(interest(:,30))
+plot(interest(:,40))

### 2015-11-16 manuscript.tex
Better formatting, more shit

@@
   backgroundcolor=\color{Background},basicstyle=\ttfamily\small\setstretch{1},breaklines=true,
-  commentstyle=\color{mygreen},emph=[1]{for,end,break},emphstyle=[1]\color{red},frame=l,identifierstyle=\color{black},
-  keywordstyle=[2]{\color{black}},keywordstyle=\color{blue},language=Matlab,literate={~} {\texttildelow}{1},
-  morekeywords=[2]{1},morekeywords={matlab2tikz},numbers=left,numbersep=9pt,numberstyle={\tiny \color{black}},
-  showstringspaces=false,stringstyle=\color{mylilas},
+  commentstyle=\color{mygreen}\slshape,emph=[1]{for,end,break},emphstyle=[1]\color{red},frame=l,identifierstyle=\color{black},
+  keywordstyle=[2]{\color{black}},keywordstyle={\color{blue}\bfseries},language=Matlab,literate={~} {\texttildelow}{1},
+  morekeywords=[2]{1},morekeywords={matlab2tikz},numbers=left,numbersep=1em,numberstyle=\footnotesize,
+  showstringspaces=false,stringstyle=\color{mylilas},xleftmargin=1em,
 }

### 2015-11-16 manuscript.tex
Better colors

--- 2015-11-16 manuscript.tex
@@
   backgroundcolor=\color{Background},basicstyle=\ttfamily\small\setstretch{1},breaklines=true,
-  commentstyle=\color{mygreen},emph=[1]{for,end,break},emphstyle=[1]\color{red},frame=l,identifierstyle=\color{black},
-  keywordstyle=[2]{\color{black}},keywordstyle=\color{blue},language=Matlab,literate={~} {\texttildelow}{1},
-  morekeywords=[2]{1},morekeywords={matlab2tikz},numbers=left,numbersep=9pt,numberstyle={\tiny \color{black}},
-  showstringspaces=false,stringstyle=\color{mylilas},
+  commentstyle=\color{Comments}\slshape,emph=[1]{for,end,break},emphstyle=[1]\color{red},frame=l,identifierstyle=\color{black},
+  keywordstyle=[2]{\color{black}},keywordstyle={\color{blue}\bfseries},language=Matlab,literate={~} {\texttildelow}{1},
+  morekeywords=[2]{1},morekeywords={matlab2tikz},numbers=left,numbersep=1em,numberstyle=\footnotesize,
+  showstringspaces=false,stringstyle=\color{Strings},xleftmargin=1em,
 }

### 2015-11-16 manuscript.tex
pushing markov section

--- 2015-11-16 manuscript.tex
@@
     \end{figure}
-    The thickness of each arrow in this graph represents the transition probability from one node to another.
-In evacuation terms, these are the proportions of a county's population that travel to a destination node during a single update.
-In order We standardize the time interval of an update to be one hour, and track the number of people in every county after each update in the 4 day period before landfall.
+    The thickness of each arrow in this graph represents the magnitue of transition probability from one node to another.
+In evacuation terms, these are the proportions of a county's population that travel to another county during a single update.
+The remaining population that does not leave a county during a single time step implicitly loops back into the same node.
+Note that for the counties along the northern border of Mississippi, this necessitates a strictly looping behavior because there are no further northern counties.
+This results in a key assumption that the evacuated population aggregates in the northernmost counties over time, where they are considered to be completely safe from the hurricane.
+\\
+    \\
+    A second key assumption is that the transition probabilities of the graph remain fixed over the entire course of the simulation.
+The real world implications of this are that county populations converge towards 0 rather than allowing for a full evacuation in a finite number of time steps.
+This is an assumption that we deem  We standardize the time for an update to be one hour, and track the number of people in every county through the 4 day period before landfall.
 
@@
   \subsection{Strengths and Weaknesses}
+    By aggregating population in the northernmost counties, this model as a limiting assumption that evacuees never leave Mississippi.
 
@@
 Instead, the category is reflected by the size of the list of the affected counties given as the respective inputs for the estimates.
-In order to generate these input, we used the historical hurricane data.
-Given the landfall and the hurricane's category, we can generate three sets of decreasing size containing neighboring counties.
-We can then run the simulation on these inputs.
   \subsection{Results}
-    This model's main goal is to find the amount of time it takes to evacuate the affected states.
     \begin{figure}
@@
       \caption{}
-      \label{}
     \end{figure}

### 2015-11-16 manuscript.tex
More on the flow

--- 2015-11-16 manuscript.tex
@@
   backgroundcolor=\color{Background},basicstyle=\ttfamily\small\setstretch{1},breaklines=true,
-  commentstyle=\color{Comments}\slshape,emph=[1]{for,end,break},emphstyle=[1]\color{red},frame=l,identifierstyle=\color{black},
-  keywordstyle=[2]{\color{black}},keywordstyle={\color{blue}\bfseries},language=Matlab,literate={~} {\texttildelow}{1},
-  morekeywords=[2]{1},morekeywords={matlab2tikz},numbers=left,numbersep=1em,numberstyle=\footnotesize,
-  showstringspaces=false,stringstyle=\color{Strings},xleftmargin=1em,
+  commentstyle=\color{mygreen},emph=[1]{for,end,break},emphstyle=[1]\color{red},frame=l,identifierstyle=\color{black},
+  keywordstyle=[2]{\color{black}},keywordstyle=\color{blue},language=Matlab,literate={~} {\texttildelow}{1},
+  morekeywords=[2]{1},morekeywords={matlab2tikz},numbers=left,numbersep=9pt,numberstyle={\tiny \color{black}},
+  showstringspaces=false,stringstyle=\color{mylilas},
 }
@@
     So according to this model, if we decided to evacuate everyone in the southern counties all at once, it would take upwards of a day to get everyone to safe counties.
+Just to be safe, we can wait until two days prior to landfall before we order county wide evacuations.
   \subsection{Strengths and Weaknesses}
-    % TODO
-    This model gives us a piece of information that no other model really touches: the roads that create a bottleneck in the evacuation.
+    This model gives us a piece of information that no other model really touches: the roads that create a bottleneck in the evacuation. % TODO FINISH THIS
+    % Weaknesses
+    This model assumes a best case scenario for the utilization of the roads, whereas in reality, people will rarely use the fastest path to a destination.
+Their behavior will make for a much slower evacuation.
+We don't really have a way to tell each car what route it should or shouldn't take in order to make the evacuation as speedy as possible, as it would mean sacrificing some drivers for the benefit of others.
 

### 2015-11-16 manuscript.tex
Added some images to manus

@@
   \subsection{Results}
+    % TODO
+      Figure~\ref{fig:pop_deter} shows the evolution of the populations of some example states during an evacuation.
+The Y-Axis shows the percentage of the original population is contained in that state, and the X-Axis is the number of hours that has elapsed since the evacuation order.
+    \begin{figure}
+      \center
+      \begin{subfigure}[b]{0.3\textwidth}
+        \center
+        \includegraphics[width=\textwidth]{figures/pop_county_29-crop.pdf}
+        \caption{Population of Jackson}
+        \label{fig:pop_county60}
+      \end{subfigure}~
+      \begin{subfigure}[b]{0.3\textwidth}
+        \center
+        \includegraphics[width=\textwidth]{figures/pop_county_39-crop.pdf}
+        \caption{Population of Leake}
+        \label{fig:pop_county39}
+      \end{subfigure}~
+      \begin{subfigure}[b]{0.3\textwidth}
+        \center
+        \includegraphics[width=\textwidth]{figures/pop_county_60-crop.pdf}
+        \caption{Population of Rankin}
+        \label{fig:pop_county60}
+      \end{subfigure}
+      \caption{Evolution of populations during evacuation}
+      \label{fig:pop_deter}
+    \end{figure}
+    % TODO
+    % We tested against all 15 hurricanes
+    % For 14 of the 15 hurricanes, we managed to have the time to evacuation under 80 minutes.
+    % One hurricane (category 5) made the evacuation take longer than 100 days --> order evacuation imediately as soon as we see a cat 5
+
   \subsection{Strengths and Weaknesses}
+    % We can get an estimate of how long we need to evacuate based on the specs of the hurricane
+    % Its not a one-size-fits all which is good and bad
     By aggregating population in the northernmost counties, this model as a limiting assumption that evacuees never leave Mississippi.

### 2015-11-16 deterministic/constantrate.m

@@ -27,4 +27,4 @@ for t=0:1:max_t
 end
 
 figure
-plot(interest(:,40))
+plot(interest(:,30))

### 2015-11-16 manuscript.tex
working on markov analysis

--- 2015-11-16 manuscript.tex
@@
 We can model our evacuation strategy by converting the network of Mississippi counties into a directed graph.
-For our northward evacuation, this means only drawing highway-based edges to destination nodes with higher latitudes:
+For our northward evacuation, this means only drawing highway-based edges toward nodes with higher latitudes:
     \begin{figure}[H]
@@
 The remaining population that does not leave a county during a single time step implicitly loops back into the same node.
+This fulfills a conservation of mass required for all Markov models, preventing population from slowing leaking out of the system.
 Note that for the counties along the northern border of Mississippi, this necessitates a strictly looping behavior because there are no further northern counties.
@@
 The real world implications of this are that county populations converge towards 0 rather than allowing for a full evacuation in a finite number of time steps.
-This is an assumption that we deem  We standardize the time for an update to be one hour, and track the number of people in every county through the 4 day period before landfall.
+We consider this assumption to be reasonable because in a real world scenario it becomes increasingly difficult to evacuate straggling population members who have a reduced mobility due to age, poverty, or other factors.
+\\
+
+    We standardize the time for an update to be one hour, and track the number of people in every county through the 4 day period before landfall.
 
@@
   \subsection{Strengths and Weaknesses}
-    By aggregating population in the northernmost counties, this model as a limiting assumption that evacuees never leave Mississippi.
+    By aggregating population in the northernmost counties, this model has a limiting assumption that evacuees never leave Mississippi.
+    In ensuring that every highway fulfills its maximum theoretical utilization, this model assumes that evacuations are disorderly and don't follow any government mandated routes.
+Every citizen is told to simply flee, and they find the path of least resistance.
+This makes this model a good baseline for comparing more though fully orchestrated plans.
+    Another strength of this model is that it intelligently decides evacuation priorities based on expected landfall.
+This allows for a more optimal solution to ensure we don't overreact to low class hurricanes, providing a minimal impact to the normal functioning of these counties.
 
@@
     So according to this model, if we decided to evacuate everyone in the southern counties all at once, it would take upwards of a day to get everyone to safe counties.
-Just to be safe, we can wait until two days prior to landfall before we order county wide evacuations.
   \subsection{Strengths and Weaknesses}
-    This model gives us a piece of information that no other model really touches: the roads that create a bottleneck in the evacuation. % TODO FINISH THIS
-    % Weaknesses
-    This model assumes a best case scenario for the utilization of the roads, whereas in reality, people will rarely use the fastest path to a destination.
-Their behavior will make for a much slower evacuation.
-We don't really have a way to tell each car what route it should or shouldn't take in order to make the evacuation as speedy as possible, as it would mean sacrificing some drivers for the benefit of others.
+    % TODO
+    This model gives us a piece of information that no other model really touches: the roads that create a bottleneck in the evacuation.
 

### 2015-11-16 manuscript.tex

--- 2015-11-16 manuscript.tex
@@
   \subsection{Strengths and Weaknesses}
+    By aggregating population in the northernmost counties, this model has a limiting assumption that evacuees never leave Mississippi.
+    In ensuring that every highway fulfills its maximum theoretical utilization, this model assumes that evacuations are disorderly and don't follow any government mandated routes.
+Every citizen is told to simply flee, and they find the path of least resistance.
+This makes this model a good baseline for comparing more though fully orchestrated plans.
+    Another strength of this model is that it intelligently decides evacuation priorities based on expected landfall.
+This allows for a more optimal solution to ensure we don't overreact to low class hurricanes, providing a minimal impact to the normal functioning of these counties.
     % We can get an estimate of how long we need to evacuate based on the specs of the hurricane

### 2015-11-16 manuscript.tex
May need touchups

@@
 
-\section{Stochastic Model of Landfall-Avodiant Evacuations}
-\label{sec:stochastic}
+\section{Heuristic Model of Landfall-Avodiant Evacuations}
+\label{sec:heuristic}
   \subsection{Model Description}
@@
 We can then run the simulation on these inputs.
+For the first 48 hours, we start to evacuate all the counties listed in the less accurate estimated, then for the second to last day we use the more accurate set of counties to pick which ones to evacuate, and finally the most accurate estimate is used for the last 24 hours.
   \subsection{Results}
-    This model's main goal is to find the amount of time it takes to evacuate the affected states.
+    \par This model's main goal is to find the amount of time it takes to evacuate the affected counties, given the estimated floods.
+After 100 simulations with the parameters described above, we find that it consistently takes less than 50 hours to evacuate all the at-risk counties.
+Figures \ref{fig:stochastic_out_large} and \ref{fig:stochastic_out_small} depict the evolution of the county populations when the impending hurricane is of category 1 and 5 respectively.
+The hurricane in Figure~\ref{fig:stochastic_out_large} is coming from the West, and a such, the population of Jackson County initially peaks as everyone moves east and directly away from the hurricane's projected landfall, then decreases as citizens start then making their way north and out of the state.
+In Figure~\ref{fig:stochastic_out_small}, the hurricane comes directly from the South.
+There is a slight flaw in the graph in that Harrison County is represented to be lower than Jackson County, and the connectivity between the two is quite high.
+As such, people from Harrison County will seek refuge in Jackson County before moving North.
+    \par There was also a large congestion observed in Greene County.
+It would seem that on their way North, citizens have trouble exiting this county.
+The model described in \nameref{sec:maxflow} concluded that adding highways in this area of Mississippi would drastically improve the flow of citizens.
+This heuristic model reflects that this is a high congestion area and supports the idea that adding roads there would increase citizen flow.
     \begin{figure}
@@
         \caption{Predicted Evacuation for Landfall in Hancock County}
+        \label{fig:stochastic_out_large}
       \end{subfigure}~
@@
         \caption{Predicted Evacuation for Landfall in Jackson County}
+        \label{fig:stochastic_out_small}
       \end{subfigure}
       \caption{}
-      \label{}
+      \label{fig:stochastic_out}
     \end{figure}
   \subsection{Strengths and Weaknesses}
+    \par There are three main weaknesses in this model, two of which are referred to above.
+The first is that this model assumes that the State of Mississippi does not make accommodations for its citizens in the northern counties, meaning that once the citizens evacuate their home counties, they are left to fend for themselves.
+But, it does mean that evacuation is very fast, since no county officials need to be involved in organizing the evacuation.
+There comes a point at which the State must leverage speed of evacuation against citizen accommodations.
+We can only help in stating that a strategy such as the one outlined in this model will likely yield quicker evacuation times, especially in times of emergency.
+    \par The other weakness is that by representing Mississippi like we have done, we prevent citizens from using smaller backroads to leave the county.
+This hinders their heuristic to move NorthWest in our simulations.
+Had we used a more accurate dataset or a more fine grid than just county geographical centers, the simulations would yield faster evacuation times, with everyone immediately going in the right direction.
 

### 2015-11-16 manuscript.tex
finished markov model description

--- 2015-11-16 manuscript.tex
@@
     Given that we have a network structure and associated population flow rates, this problem lends itself well to a Markov process analysis.
-We can model our evacuation strategy by converting the network of Mississippi counties into a directed graph.
-For our northward evacuation, this means only drawing highway-based edges toward nodes with higher latitudes:
+We can then model our evacuation strategy by converting the network of Mississippi counties into a directed graph.
+For our northward evacuation, this means only drawing highway-directed edges toward nodes with higher latitudes:
     \begin{figure}[H]
@@
 The remaining population that does not leave a county during a single time step implicitly loops back into the same node.
-This fulfills a conservation of mass required for all Markov models, preventing population from slowing leaking out of the system.
+This fulfills a conservation of probability required for all Markov models, preventing population from slowing leaking out of the system.
 Note that for the counties along the northern border of Mississippi, this necessitates a strictly looping behavior because there are no further northern counties.
@@
     A second key assumption is that the transition probabilities of the graph remain fixed over the entire course of the simulation.
-The real world implications of this are that county populations converge towards 0 rather than allowing for a full evacuation in a finite number of time steps.
-We consider this assumption to be reasonable because in a real world scenario it becomes increasingly difficult to evacuate straggling population members who have a reduced mobility due to age, poverty, or other factors.
+The real world implications of this are that county populations converge toward 0 rather than allowing for a full evacuation in a finite number of time steps.
+We consider this assumption to be reasonable because in a real world scenario it becomes increasingly difficult to evacuate straggling population members who have a reduced mobility due to age, poverty, and/or other factors.
 \\
 
-    We standardize the time for an update to be one hour, and track the number of people in every county through the 4 day period before landfall.
+    In order to run this algorithm, we first initialize a vector of county populations and matrix of transition probabilities.
+While the initial county populations are drawn from census data \cite{census},justifications for the transition probabilities can be found in the next section.
+We standard the time step for an update to be one hour such that multiplying the transition matrix and the current population vector gives the population distribution at the next hour.
+We do this until one of two termination criteria are met:
+    \begin{itemize}
+      \item[1.]
+        The hurricane arrives after 96 time steps
+      \item[2.]
+        All population counts are below a predetermined, county-specific threshold
+    \end{itemize}
+
+    Once the termination occurs, we evaluate the success of the evacuation in relation to our quotas determined by predicted landfall of a hurricane.
+This hurricane will be one randomly chosen from those found from historical data.
+If population thresholds are not met within the full 4 day advance notice period, we suggest that the state be evacuated at first warning.
+Otherwise, evacuate in advance the number of hours required to meet the desired thresholds.
 
@@
     By aggregating population in the northernmost counties, this model as a limiting assumption that evacuees never leave Mississippi.
+    Weakness that people flee even if they are aleady in the safe zone.
+    Weak in the
 

### 2015-11-16 manuscript.tex
Some threshold shit

--- 2015-11-16 manuscript.tex
@@
     Given that we have a network structure and associated population flow rates, this problem lends itself well to a Markov process analysis.
-We can then model our evacuation strategy by converting the network of Mississippi counties into a directed graph.
-For our northward evacuation, this means only drawing highway-directed edges toward nodes with higher latitudes:
+We can model our evacuation strategy by converting the network of Mississippi counties into a directed graph.
+For our northward evacuation, this means only drawing highway-based edges toward nodes with higher latitudes:
     \begin{figure}[H]
@@
 The remaining population that does not leave a county during a single time step implicitly loops back into the same node.
-This fulfills a conservation of probability required for all Markov models, preventing population from slowing leaking out of the system.
+This fulfills a conservation of mass required for all Markov models, preventing population from slowing leaking out of the system.
 Note that for the counties along the northern border of Mississippi, this necessitates a strictly looping behavior because there are no further northern counties.
@@
     A second key assumption is that the transition probabilities of the graph remain fixed over the entire course of the simulation.
-The real world implications of this are that county populations converge toward 0 rather than allowing for a full evacuation in a finite number of time steps.
-We consider this assumption to be reasonable because in a real world scenario it becomes increasingly difficult to evacuate straggling population members who have a reduced mobility due to age, poverty, and/or other factors.
+The real world implications of this are that county populations converge towards 0 rather than allowing for a full evacuation in a finite number of time steps.
+We consider this assumption to be reasonable because in a real world scenario it becomes increasingly difficult to evacuate straggling population members who have a reduced mobility due to age, poverty, or other factors.
 \\
 
-    In order to run this algorithm, we first initialize a vector of county populations and matrix of transition probabilities.
-While the initial county populations are drawn from census data \cite{census},justifications for the transition probabilities can be found in the next section.
-We standard the time step for an update to be one hour such that multiplying the transition matrix and the current population vector gives the population distribution at the next hour.
-We do this until one of two termination criteria are met:
-    \begin{itemize}
-      \item[1.]
-        The hurricane arrives after 96 time steps
-      \item[2.]
-        All population counts are below a predetermined, county-specific threshold
-    \end{itemize}
-
-    Once the termination occurs, we evaluate the success of the evacuation in relation to our quotas determined by predicted landfall of a hurricane.
-This hurricane will be one randomly chosen from those found from historical data.
-If population thresholds are not met within the full 4 day advance notice period, we suggest that the state be evacuated at first warning.
-Otherwise, evacuate in advance the number of hours required to meet the desired thresholds.
+    We standardize the time for an update to be one hour, and track the number of people in every county through the 4 day period before landfall.
 
@@
     Using our earlier values for the maximum flow rate of an edge, we can now use this
+
+    In order to get the threshold for each county based on the hurricane characteristics, we created a function that would give us the proportion of the original population that did not need to be evacuated.
+For instance, during a category 1 hurricane, we would find it acceptable to only evacuate 50\% of the original population.
+Similarily, the proximity of the county in question should factor into that threshold.
+    The formula we ended up using is the following:
+    \begin{align*}
+        threshold(c, h) = 0.1 \cdot 2^{||c-h||_2 / h.radius} \cdot \frac{1}{h.category}
+    \end{align*}
+    In addition to this, if a county is further away than 3 times the radius of the hurricane, that county does not need to be evacuated, and we tag it as a refugee state (it essentially has infinite threshold).
+Furthermore, category 1 hurricanes have a threshold minimum of 50\% (we do not require more than half of the population of any county to evacuate).
+    The heatmaps for those thresholds can be observed in Figure~\ref{fig:thresholds}.
+These were generated from a category 1 hurricane (a) that then grows in size (b) and finally becomes category 5 (c).
+    \begin{figure}
+      \center
+      \begin{subfigure}[b]{0.3\textwidth}
+        \center
+        \includegraphics[width=\textwidth]{figures/right_73_1-crop.pdf}
+        \caption{Radius: 73km - Category 1}
+        \label{fig:pop_county60}
+      \end{subfigure}~
+      \begin{subfigure}[b]{0.3\textwidth}
+        \center
+        \includegraphics[width=\textwidth]{figures/right_120_1-crop.pdf}
+        \caption{Radius: 120km - Category 1}
+        \label{fig:pop_county39}
+      \end{subfigure}~
+      \begin{subfigure}[b]{0.3\textwidth}
+        \center
+        \includegraphics[width=\textwidth]{figures/right_120_5-crop.pdf}
+        \caption{Radius: 120km - Category 5}
+        \label{fig:pop_county60}
+      \end{subfigure}
+      \caption{Thresholds of evacuation for counties of Mississippi}
+      \label{fig:thresholds}
+    \end{figure}
+
   \subsection{Results}
@@
     By aggregating population in the northernmost counties, this model as a limiting assumption that evacuees never leave Mississippi.
-    Weakness that people flee even if they are aleady in the safe zone.
-    Weak in the
 

### 2015-11-16 manuscript.tex
typos

--- 2015-11-16 manuscript.tex
@@
 \label{sec:markov}
-  Because our analysis of historical hurricane trends concluded that the vast majority of landfalls occur in the three southern-most counties, the first evacuation strategy we tested was one where all evacuees move strictly northward.
+  Because our analysis of historical hurricane trends concluded that the vast majority of landfalls occur in the three southern-most counties, the first evacuation strategy we tested was one in which all evacuees move strictly northward.
   \subsection{Model Description}
@@
     \end{figure}
-    The thickness of each arrow in this graph represents the magnitue of transition probability from one node to another.
+    The thickness of each arrow in this graph represents the magnitude of transition probability from one node to another.
 In evacuation terms, these are the proportions of a county's population that travel to another county during a single update.

### 2015-11-16 manuscript.tex
Added start of contributions section

--- 2015-11-16 manuscript.tex
@@
 \label{sec:contributions}
+\subsection*{Ryan}
+Performed the data-fetching of the hurricanes. Wrote all of the most of the manuscript with Paul. Worked out some of the logic for both the flow and the markov model.
+
+\subsection*{Paul}
+Designed and implemented the stochastic model. Helped Ryan write most of the manuscript. Parsed the county data such as county location and population using the WolframAlpha API.
+
+\subsection*{Antoine}
+Implemented the flow and Markov models. Created almost all of the graph and network visualizations. Worked on the two first models' analyses for the manuscript.
+
   \begin{thebibliography}{9}

### 2015-11-16 manuscript.tex
moved pictures

--- 2015-11-16 manuscript.tex
@@
   \subsection{Parameter Values and Justification}
-    Using our earlier values for the maximum flow rate of an edge, we can now use this
-
+    Using our earlier values for the maximum flow rate of an edge, we can now use them to derive transition probabilities for our Markov model.
+Because the maximum capacity of a road is 3000 times it's weight in the graph, this can be used to give the total population emanating from a county in the first hour of the simulation.
+If we find the ratios of these values along each edge to the initial population in the county, this gives us a good approximation of the percentage of a county that flees in any given time step.
+Again we assume these proportions are constant for each edge and ensure conservation of probability through the whole graph.
+We ensured this conservation of probability by ensuring a constant population throughout the state at every time step.\\
+    \\
     In order to get the threshold for each county based on the hurricane characteristics, we created a function that would give us the proportion of the original population that did not need to be evacuated.
 For instance, during a category 1 hurricane, we would find it acceptable to only evacuate 50\% of the original population.
-Similarily, the proximity of the county in question should factor into that threshold.
+Similarly, the proximity of the county in question should factor into that threshold.
     The formula we ended up using is the following:
@@
 These were generated from a category 1 hurricane (a) that then grows in size (b) and finally becomes category 5 (c).
-    \begin{figure}
+    \begin{figure}[H]
       \center
@@
 The Y-Axis shows the percentage of the original population is contained in that state, and the X-Axis is the number of hours that has elapsed since the evacuation order.
-    \begin{figure}
+    \begin{figure}[H]
       \center

### 2015-11-16 manuscript.tex
Added future works

--- 2015-11-16 manuscript.tex
@@
 \label{sec:future}
+The first aspect that we would like to focus on in the future had we had more time would be the interactions between Mississippi and its surrounding states.
+It is probable that in the event of a state wide evacuation, the transportation system would need to support not just the citizens of Mississippi but also those of Louisiana and Alabama.
+\newline
+In addition to this, we would like to do more robustness testing by generating random hurricanes and their trajectories, and plan accordingly.
+This would allow us to test on a much bigger data sample than the one we were able to get our hands on.
+\newline
+Another area that we would have liked to improve has to do with the fact that we did not take into account the trajectory of the hurricanes after they made landfall.
+We considered that by that time, the populations of the counties affected should have been evacuated according to the level of emergency that we assigned them.\newline
+Overall, all of these would be achievable with the state of our models, but would require a lot of time to polish as it would add a significant amount of complexity to the simulations.
 

### 2015-11-16 manuscript.tex
Added missing edge

@@
 
-\section{Heuristic Model of Landfall-Avodiant Evacuations}
+\section{Heuristic Model of Landfall-Avoiding Evacuations}
 \label{sec:heuristic}
@@
 After 100 simulations with the parameters described above, we find that it consistently takes less than 50 hours to evacuate all the at-risk counties.
-Figures \ref{fig:stochastic_out_large} and \ref{fig:stochastic_out_small} depict the evolution of the county populations when the impending hurricane is of category 1 and 5 respectively.
+Figures \ref{fig:stochastic_out_large} and \ref{fig:stochastic_out_small} depict the evolution of the county populations when the impending hurricane is of category 5 and 1 respectively.
 The hurricane in Figure~\ref{fig:stochastic_out_large} is coming from the West, and a such, the population of Jackson County initially peaks as everyone moves east and directly away from the hurricane's projected landfall, then decreases as citizens start then making their way north and out of the state.
@@
       \end{subfigure}
-      \caption{}
+      \caption{Evacuation Comparison for Category 5 and 1 Hurricanes}
       \label{fig:stochastic_out}
@@
 \label{sec:conclusions}
+\par The first thing that we want to conclude on is that two of our models agree on the fact that there is a large amount of congestion in the Southern area of Mississippi.
+Congestion in this area is not ideal, and in fact dangerous, since it is the area most likely to be flooded by hurricanes.
+This congestion seems to be caused by a lack of highway coverage in the Southwestern part of Mississippi, especially between Stone, Perry, Greene and George counties.
+In fact, adding a Four-Lane Highway between George and Perry Counties moves the bottleneck of traffic flow to a considerably safer area up North.
+Our strongest recommendation to the State of Mississippi, as  a preventative measure, is to consider such a highway.\\
+
+\par Finally, we can conclude on the strategy to use, depending on the situation.
+The Heuristic Model is a model where all citizens decide where they are going on their own, and in which county officials do not need to intervene.
+As such, this model leads to the highest evacuation speeds, at the cost of having a place for the citizens to take refuge.
+Therefore this strategy should only be used in the most urgent scenario, where everyone absolutely must leave the affected counties as quickly as possible.
+On the other hand, if the State has had more time to prepare and has forecasted the arrival of the hurricane early enough, then they can tell the citizens to stay in-state, make accommodations for them, and give them very specific routes according to either the Markov Model or the Maxflow Model.
+This is a more heavy-handed strategy and would invariably involve a lot of intervention from the county officials in order to properly organize the evacuations.
 
@@
 \subsection*{Ryan}
-Performed the data-fetching of the hurricanes. Wrote all of the most of the manuscript with Paul. Worked out some of the logic for both the flow and the markov model.
+Performed the data-fetching of the hurricanes. Wrote all of the most of the manuscript with Paul. Worked out some of the logic for both the flow and the Markov model.
 
 \subsection*{Paul}
-Designed and implemented the stochastic model. Helped Ryan write most of the manuscript. Parsed the county data such as county location and population using the WolframAlpha API.
+Designed and implemented the stochastic model.
+Helped Ryan write most of the manuscript.
+Parsed the county data such as county location and population using the WolframAlpha API.
+Created the Mississippi Highway map used in all the models.
 

### 2015-11-16 manuscript.tex
nothing to see here

--- 2015-11-16 manuscript.tex
@@
 Given that this coastal area is a strong commercial center, the government authorities want us to minimize the number of unnecessary evacuations.
-Under this requirement, it is more advantageous to withhold ordering an evacuation for as long as safely possible.
+Under this requirement, it is more advantageous to withhold ordering an evacuation for as long as is safely possible.
 The reasons for this are two-fold.
@@
 \label{sec:future}
-The first aspect that we would like to focus on in the future had we had more time would be the interactions between Mississippi and its surrounding states.
-It is probable that in the event of a state wide evacuation, the transportation system would need to support not just the citizens of Mississippi but also those of Louisiana and Alabama.
-\newline
-In addition to this, we would like to do more robustness testing by generating random hurricanes and their trajectories, and plan accordingly.
-This would allow us to test on a much bigger data sample than the one we were able to get our hands on.
-\newline
-Another area that we would have liked to improve has to do with the fact that we did not take into account the trajectory of the hurricanes after they made landfall.
-We considered that by that time, the populations of the counties affected should have been evacuated according to the level of emergency that we assigned them.\newline
-Overall, all of these would be achievable with the state of our models, but would require a lot of time to polish as it would add a significant amount of complexity to the simulations.
 

### 2015-11-16 manuscript.tex
Wamp wamp
Added some things to contributions
Brought back cropped

--- 2015-11-16 manuscript.tex
@@
       \center
-      \includegraphics[width=\linewidth]{figures/full_undirected-crop.pdf}
+      \includegraphics[width=\linewidth]{figures/full_undirected.pdf}
       \caption*{Undirected Graph Representing Mississippi Counties}
@@
         \center
-        \includegraphics[width=\textwidth]{figures/right_73_1-crop.pdf}
+        \includegraphics[width=\textwidth]{figures/right_73_1.pdf}
         \caption{Radius: 73km - Category 1}
@@
         \center
-        \includegraphics[width=\textwidth]{figures/right_120_1-crop.pdf}
+        \includegraphics[width=\textwidth]{figures/right_120_1.pdf}
         \caption{Radius: 120km - Category 1}
@@
         \center
-        \includegraphics[width=\textwidth]{figures/right_120_5-crop.pdf}
+        \includegraphics[width=\textwidth]{figures/right_120_5.pdf}
         \caption{Radius: 120km - Category 5}
@@
 \subsection*{Antoine}
-Implemented the flow and Markov models. Created almost all of the graph and network visualizations. Worked on the two first models' analyses for the manuscript.
+Implemented the flow and Markov models.
+Created almost all of the graph and network visualizations.
+Worked on the two first models' analyses for the manuscript.
+Wrote the Future Work section and the Individual Contributions.
 

### 2015-11-16 manuscript.tex
done executive summary

--- 2015-11-16 manuscript.tex
@@
 \label{sec:summary}
+Governor Bryant,\\
+
+At the request of the Mississippi Emergency Management Administration, we have conducted a thorough mathematical analysis of hurricane evacuation strategies for all 82 counties in the state of Mississippi.
+These strategies were tested across a range of possible hurricane conditions backed by historical weather data.
+By testing across this range of possibilities, we found that it is best to follow one of two different strategies depending on the type of storm being faced.\\
+
+In the event of a moderately sized, category 1, 2, or 3 hurricane, we recommend a strategy of evacuating every county in the coastal region.
+These evacuations should head in a direction that is most pointed away from the expected landfall.
+If many of the direction choices are very similar, these counties should prefer their north-west neighbors, as hurricanes from the gulf tend to curve toward the north-east.
+The virtues of this strategy are that it's relatively localized and allows each county to independently pick it's evacuation direction.
+As a result of this, evacuations of this type are very quick to organize, and allow for a rapid evacuation of the most endangered areas.
+This is useful for moderately sized hurricanes because it allows you to take more time in deciding whether or not to evacuate.
+You can wait to see if the storm will die down before hitting the coast, but are still able to spring into action if it doesn't.\\
+
+In the event of a very large, category 4 or 5 hurricane, we recommend an orderly evacuation of the entire lower half of Mississippi toward the northern border.
+If a storm of this type appears on the radar, it is very unlikely to die down before hitting the coast, and is more likely to pass over Mississippi with its increased size.
+Strong governmental organization is required as early as possible to prevent a catastrophic loss of life.
+We have code capable of solving for the optimal allocation of traffic on each highway to maximize the throughput of the entire evacuation.
+This is a very heavy-handed response that should be reserved for the most dire of circumstances.
+In this event that this is needed, we encourage you to consult us for a solution tailored to that specific storm.\\
+
+While these two strategies can aid you in making decisions for an imminent hurricane, we also have a recommendation for a long-term improvement to all evacuation routes.
+In our analysis of evacuation throughput, we discovered that the area around George County poses a significant bottleneck for highway traffic.
+As our analysis will show later in this manuscript, adding an additional highway route from George County to Perry county will significantly shift this bottleneck upward.
+This would allow more evacuees to escape the most dangerous coastal areas before they are slowed down by a bottleneck.
+Especially with potentially heavy traffic coming up highway 59 from New Orleans, traffic congestion in the coastal region is a problem requiring a more long term solution.
 

### 2015-11-16 manuscript.tex
intro done

@@
 \label{sec:summary}
+\\
 Governor Bryant,\\
@@
 This would allow more evacuees to escape the most dangerous coastal areas before they are slowed down by a bottleneck.
-Especially with potentially heavy traffic coming up highway 59 from New Orleans, traffic congestion in the coastal region is a problem requiring a more long term solution.
+Especially with potentially heavy traffic coming up highway 59 from New Orleans, traffic congestion in the coastal region is a problem requiring a more long term solution.\\
+\\
+\\
+Sincerely,\\
+Paul Chesnais, Antoine Pourchet, and Ryan Vogan
 
+\newpage
 \section{Introduction}
@@
 Given that this coastal area is a strong commercial center, the government authorities want us to minimize the number of unnecessary evacuations.
-Under this requirement, it is more advantageous to withhold ordering an evacuation for as long as is safely possible.
+Under this requirement, it is more advantageous to withhold evacuations for as long as safely possible.
 The reasons for this are two-fold.
 First, this ensures that local businesses can remain open for as long as possible.
-Second, this ensures that the forecasts at the time of the evacuation decision are as accurate as possible.
+Second, this ensures that evacuation decisions are made when forecasts are most accurate.
 Therefore, our models seek to recommend an optimal evacuation plan as well as the latest possible time at which it is safe to enact this plan.

### 2015-11-16 manuscript.tex
network representation done

@@
   \par
-     Because Mississippi has varying highway structure, it would be inappropriate to assume uniform travel rates between county pairs.
+     Because Mississippi has varying highway structure, it would be inappropriate to assume uniform travel rates between all county pairs.
 In order to capture this heterogeneity in the network model, we decided to assign weights to every edge.
-Then a single edge weight represents a carrying capacity for the amount of travel possible between two counties.
-For a real-world mapping, we assume that this would correspond to the total number of highway lanes spanning two counties.
+Then a single edge weight represents a carrying capacity for the maximum amount of travel between two counties.
+For a real-world mapping of this, we assume that this would correspond to the total number of highway lanes spanning two counties.
 Therefore, we were able to assign edge weights across the entire graph by using the following highway map:

### 2015-11-16 manuscript.tex
Hurricane History Done

@@
 \label{sec:summary}
-\\
+\vspace{1cm}
 Governor Bryant,\\
@@
 \label{sec:hurricanes}
-  \par
-    Northwest
+  Before designing potential evacuation strategies, we first sought to understand the expected speed, size, and landfall of a hurricane impacting Mississippi.
+Discovering patterns in these storms proved very difficult, because the Earth's atmosphere is a chaotic system.
+Other than the general pattern that hurricanes in the Gulf of Mexico tend to curl back toward the north-east, there is very little we can predict about a hurricane's trajectory:
+   \begin{figure}[H]
+    \centering
+      \includegraphics[width=.5\textwidth]{figures/chaos.jpg}
+      \caption{Map of Atlantic Hurricane Trajectories \cite{chaos}}
+    \end{figure}
+  As a result of this, we decided to test our evacuation plans against hurricanes that actually occurred in the past.
+This ensures that our model parameters governing the hurricane are as accurate as possible.
+In order to do this, we parsed a NOAA dataset containing every cyclone (tropical storm, hurricane, etc.) occurring from 1851 to 2014.
+For each hurricane in this dataset, we found the first latitude and longitude datapoint over Mississippi and recorded that as a landfall position (throwing out hurricanes that never passed over Mississippi).
+You can see these points in the figures below, where the left is a web-app display of hurricane trajectories over Mississippi, while the right is the 15 discovered landfalls we pulled from the NOAA dataset:
+    \begin{figure}[H]
+      \center
+      \begin{subfigure}[b]{0.5\textwidth}
+        \center
+        \includegraphics[width=\linewidth]{figures/smaller_chaos.png}
+        \caption*{Map of Mississippi Hurricane Trajectories \cite{smaller_chaos}}
+      \end{subfigure}~
+      \begin{subfigure}[b]{0.5\textwidth}
+        \center
+        \includegraphics[width=\linewidth]{figures/parsed_chaos.png}
+        \caption*{Landfall Locations Parsed From Hurricane Dataset \cite{fifteen}}
+      \end{subfigure}
+    \end{figure}
+    \newpage
+  Each point in this dataset had an associated wind speed that we used to classify it's category \cite{categories}:
+  \begin{itemize}
+    \item[]
+      \textbf{Category 1:} 74-95 mph
+    \item[]
+      \textbf{Category 2:} 96-110 mph
+    \item[]
+      \textbf{Category 3:} 111-129 mph
+    \item[]
+      \textbf{Category 4:} 130-156 mph
+    \item[]
+      \textbf{Category 5:} 157 mph or higher
+  \end{itemize}
+  The last piece of data we needed for these hurricanes were their radii.
+Since hurricane radii records don't exist for years earlier than 2004, we used a least squares linear fit to interpolate the radius for a given hurricane wind speed:
+  \begin{figure}[H]
+    \centering
+    \includegraphics[width=\textwidth]{figures/least_fit.png}
+    \caption{Hurricane Radius (nmi) vs Wind Speed (kt)}
+    \label{fig:highway_map}
+  \end{figure}
 
@@
 This heuristic model reflects that this is a high congestion area and supports the idea that adding roads there would increase citizen flow.
-    \begin{figure}
+    \begin{figure}[H]
       \center
@@
       \url{https://www.mississippi.org/assets/docs/library/ms_highways.pdf}
+    \bibitem{chaos}
+      \url{http://www.mapcruzin.com/images/hurricane-shapefile-400x255.png}
+    \bibitem{smaller_chaos}
+      \url{https://coast.noaa.gov/hurricanes/}
+    \bibitem{fifteen}
+      \url{http://www.aoml.noaa.gov/hrd/hurdat/Data_Storm.html}
+    \bibitem{categories}
+      \url{http://www.nhc.noaa.gov/aboutsshws.php}
+
     \bibitem{pmc}

### 2015-11-16 manuscript.tex
markov

@@
     \end{figure}
-    The thickness of each arrow in this graph represents the magnitude of transition probability from one node to another.
+    The thickness of each arrow in this graph represents the magnitude of a transition probability from one node to another.
 In evacuation terms, these are the proportions of a county's population that travel to another county during a single update.
-The remaining population that does not leave a county during a single time step implicitly loops back into the same node.
-This fulfills a conservation of probability required for all Markov models, preventing population from slowing leaking out of the system.
+The remaining population that does not leave a county during a single step implicitly loops back into the same node.
+This fulfills the conservation of probability required for all Markov models, preventing population from slowing leaking out of the system.
 Note that for the counties along the northern border of Mississippi, this necessitates a strictly looping behavior because there are no further northern counties.
@@
 The real world implications of this are that county populations converge toward 0 rather than allowing for a full evacuation in a finite number of time steps.
-We consider this assumption to be reasonable because in a real world scenario it becomes increasingly difficult to evacuate straggling population members who have a reduced mobility due to age, poverty, and/or other factors.
+We consider this assumption to be reasonable because in a real world scenario it becomes increasingly difficult to evacuate straggling population members who have a reduced mobility due to age, poverty, or other factors.
 \\
@@
     In order to run this algorithm, we first initialize a vector of county populations and matrix of transition probabilities.
-While the initial county populations are drawn from census data \cite{census},justifications for the transition probabilities can be found in the next section.
-We standard the time step for an update to be one hour such that multiplying the transition matrix and the current population vector gives the population distribution at the next hour.
+While the initial county populations are drawn from census data \cite{census}, justifications for the transition probabilities can be found in the next section.
+We standardize the time step for an update to be one hour such that multiplying the transition matrix and the current population vector gives the population distribution at the next hour.
 We do this until one of two termination criteria are met:
@@
 
-    Once the termination occurs, we evaluate the success of the evacuation in relation to our quotas determined by predicted landfall of a hurricane.
-This hurricane will be one randomly chosen from those found from historical data.
+    Once termination occurs, we evaluate the number of people evacuated in relation to quotas we determine using predicted landfall of a hurricane.
+This hurricane will be one randomly chosen from historical data.
 If population thresholds are not met within the full 4 day advance notice period, we suggest that the state be evacuated at first warning.
@@
   \subsection{Parameter Values and Justification}
-    Using our earlier values for the maximum flow rate of an edge, we can now use them to derive transition probabilities for our Markov model.
-Because the maximum capacity of a road is 3000 times it's weight in the graph, this can be used to give the total population emanating from a county in the first hour of the simulation.
-If we find the ratios of these values along each edge to the initial population in the county, this gives us a good approximation of the percentage of a county that flees in any given time step.
+    With our earlier values for the maximum flow rate of an edge, we can now use them to derive transition probabilities for our Markov model.
+Because the maximum capacity of a road is 3000 times its weight in the graph, this can be used to give the total population emanating from a county in the first hour of the simulation.
+If we find the ratio of these values along each emanating edge to the initial county population, this gives us a good approximation of the percentage of a county that flees in any given time step.
 Again we assume these proportions are constant for each edge and ensure conservation of probability through the whole graph.
-We ensured this conservation of probability by ensuring a constant population throughout the state at every time step.\\
+We check conservation of probability by checking that the total population remains constant throughout the simulation.\\
     \\
@@
 For instance, during a category 1 hurricane, we would find it acceptable to only evacuate 50\% of the original population.
-Similarly, the proximity of the county in question should factor into that threshold.
+In addition to this, we required that the proximity of the county in question should factor into that threshold.
 The formula we ended up using is the following:
@@
     \end{align*}
-    In addition to this, if a county is further away than 3 times the radius of the hurricane, that county does not need to be evacuated, and we tag it as a refugee state (it essentially has infinite threshold).
+    Where c is the position of the county we are considering, h is the center of the predicted hurricane, and h.category is the category of the predicted hurricane.
+The relationship between these variables was chosen so that distance from the landfall would dominate the evacuation requirements, but they still get scaled by the category.This formula only applies for county coordinates within 3 hurricane radii of the landfall.
+If a county is further away than 3 times the radius of the hurricane, that county does not need to be evacuated, and we tag it as a refugee state (it essentially has infinite threshold).
 Furthermore, category 1 hurricanes have a threshold minimum of 50\% (we do not require more than half of the population of any county to evacuate).
@@
 These were generated from a category 1 hurricane (a) that then grows in size (b) and finally becomes category 5 (c).
+Red nodes indicate counties where a majority of the population needs to be evacuated.
+Green nodes represent counties that are safe from significant hurricane damage:
     \begin{figure}[H]
@@
     \end{figure}
-    % TODO
-    % We tested against all 15 hurricanes
-    % For 14 of the 15 hurricanes, we managed to have the time to evacuation under 80 minutes.
-    % One hurricane (category 5) made the evacuation take longer than 100 days --> order evacuation imediately as soon as we see a cat 5
+
+    Running our test algorithm across all 15 hurricanes in our historical dataset, we found that 14 out of the 15 satisfied their threshold requirements within 80 hours of the evacuation start.
+Our recommendation for these hurricanes is to start the evacuation 80 hours before expected landfall.
+The one exception to this was a category 5 hurricane in the dataset.
+This hurricane took over 100 days to see the desired evacuation percentages, so we recommend an immediate and full evacuation.
 
   \subsection{Strengths and Weaknesses}
-    By aggregating population in the northernmost counties, this model has a limiting assumption that evacuees never leave Mississippi.
+    A weakness of this model is that by aggregating population in the northernmost counties, we have a limiting assumption that evacuees never leave Mississippi.
+In reality they may want to flee to Arkansas or Alabama, rather then going all the way to the top of Mississippi.
+Also by having nonzero transition probabilities on every edge, citizens may flee northward when they are already in a safe zone.\\
+    \\
     In ensuring that every highway fulfills its maximum theoretical utilization, this model assumes that evacuations are disorderly and don't follow any government mandated routes.
 Every citizen is told to simply flee, and they find the path of least resistance.
-This makes this model a good baseline for comparing more though fully orchestrated plans.
+This makes this model a good baseline for comparing more though fully orchestrated plans.\\
+    \\
     Another strength of this model is that it intelligently decides evacuation priorities based on expected landfall.
 This allows for a more optimal solution to ensure we don't overreact to low class hurricanes, providing a minimal impact to the normal functioning of these counties.
-    % We can get an estimate of how long we need to evacuate based on the specs of the hurricane
-    % Its not a one-size-fits all which is good and bad
-    By aggregating population in the northernmost counties, this model as a limiting assumption that evacuees never leave Mississippi.
-    Weakness that people flee even if they are aleady in the safe zone.
-    Weak in the
 

### 2015-11-16 manuscript.tex
maxflow done

@@
 \label{sec:maxflow}
+  After designing our first model, we realized that it was a naive assumption to have every road carrying traffic its maximum capacity.
+Actual flow rates would be dependent upon network structure as a whole and the resulting congestion.
+Because of this, we decided to perform a maximum flow analysis on our earlier strategy of evacuees moving northward.
   \subsection{Model Description}
-    \par In this model, we will approach as a network flow problem.
+    \par In this model, we will use the same approach of a network flow problem.
 The nodes of this graph will be the counties, and the edges are the roads connecting them together.
 Since we also have a quantifiable way to compare roads based on their potential throughput, we can label those as the capacities of the edges.
-    In order to get an idea of how many people can evacuate in a northbound manner, we can compute the maximum flow of the network.
-The location of the dividing line between the two partitions will also tell us the areas sof congestions, which will lead us to interesting plans.
+In order to evaluate a south to north maximum flow, we add a super source node below our north-bound graph and connect it to every county on the coast using edges of infinite capacity.
+Similarly, we connect every county along the northern border of Mississippi to a super sink node using edges of infinite capacity.
+In order to get an idea of how many people can evacuate in a northbound manner, we can compute the maximum flow of this new network.
+The location of the dividing line between the two partitions will also tell us the areas of highest traffic congestion.
+This is because a maximum flow algorithm finds the minimum sized cut to partition a graph.
+Because all traffic entering the second partition must cross this cut, it represents a bottleneck for the flow.
   \subsection{Parameter Values and Justification}
@@
 After a lot of research, we saw that more often than not, going northbound was the best reaction to most hurricanes in Mississippi (because most of the hurricanes made landfall on the south coast).
-    We also add two nodes to that graph that will act as the source and the sink (which are necessary for computing the maximum flow through the graph).
-    \par It is worth noting that we did not consider the interactions with the other states as that would require knowing a lot more things about the highway systems and tendencies of the evacuees in those states.
+It is worth noting that we did not consider the interactions with the other states as that would require knowing a lot more things about the highway systems and tendencies of the evacuees in those states.
 We also assumed that the counties that would need to be evacuated are the ones on the southern border of Mississippi; we will call them the evacuated counties.
@@
 Since the units of road are all integers, we expected an integer as the maximum flow through the graph (South to North), and that value turned out to be 21000 people moving in that direction per hour.
-The partitions are shown in red and blue in Figure~\ref{fig:oldmaxflow}.
+The partitions are shown in red and blue in Figure9 .
   \par The interesting part, though, is that this information tells us where the bottleneck is in terms of transportation.
 By inspection, we can see that a new road linking counties 20 and 56 (George to Perry, located on the south east corner of the state) could increase the maximum flow number, as well as push the congestion areas further north (which means people can get further away from the hurricanes faster).
-  Indeed, after making this change, the max flow increased by over 25\% to 27000, and the partitions split much further north than before the addition of that road. Figure~\ref{fig:newmaxflow}
-    \begin{figure}
+  Indeed, after making this change, the max flow increased by over 25\% to 27000, and the partitions split much further north than before the addition of that road.
+    \begin{figure}[H]
       \center
@@
         \center
-        \includegraphics[width=\textwidth]{figures/old_maxflow-crop.pdf}
-        \caption{Maximum Flow Partitions}
+        \includegraphics[width=.5\textwidth]{figures/old_maxflow-crop.pdf}
+        \caption*{Maximum Flow Partitions}
         \label{fig:oldmaxflow}
@@
         \center
-        \includegraphics[width=\textwidth]{figures/maxflow_directed-crop.pdf}
-        \caption{Maximum Flow Partitions}
+        \includegraphics[width=.5\textwidth]{figures/maxflow_directed-crop.pdf}
+        \caption*{Maximum Flow Partitions With George-Perry Connection}
         \label{fig:newmaxflow}
@@
 Just to be safe, we can wait until two days prior to landfall before we order county wide evacuations.
+Because maximum flow algorithms can return the amount of flow traveling across every edge in the network, we can use this to set the traffic rates/evacuation routes for every highway connection.
+While this would require a great deal of government coordination, itts optimality guarantees
+
   \subsection{Strengths and Weaknesses}
-    This model gives us a piece of information that no other model really touches: the roads that create a bottleneck in the evacuation. % TODO FINISH THIS
-    % Weaknesses
-    This model assumes a best case scenario for the utilization of the roads, whereas in reality, people will rarely use the fastest path to a destination.
+    A great strength of this model is that it leverages an algorithm who's result is provably optimal.
+Rather than giving a general strategy to the governor, this allows us to specify the traffic that should be flowing across every single highway.
+Another strength is that it gives us a piece of information that no other model really touches: the roads that create a bottleneck in the evacuation.\\
+    \\
+    Potential downsides are that this model assumes a best case scenario for the utilization of the roads, whereas in reality, people will rarely use the fastest path to a destination.
 Their behavior will make for a much slower evacuation.
-We don't really have a way to tell each car what route it should or shouldn't take in order to make the evacuation as speedy as possible, as it would mean sacrificing some drivers for the benefit of others.
+Also, we don't really have a way to tell each car what route it should or shouldn't take in order to make the evacuation as speedy as possible, as it would mean sacrificing some drivers for the benefit of Pareto-optimality.
 

### 2015-11-16 manuscript.tex
DONE

@@
     \par In this model, instead of giving citizens particular evacuation plan, we give them a simple rule: move directly away from the hurricane landfall if possible, else move North or North-West.
-Using the statewide broadcast system, the state of Mississippi can tell its citizens where the expected landfall will be, and which counties will be the most affected.
+Using and assumed statewide broadcast system, the state of Mississippi can tell its citizens where the expected landfall will be, and which counties will be the most affected.
 In which case, individual citizens are instructed to leave the counties that will be flooded, and to do so as outlined above.
@@
 \subsection*{Ryan}
-Performed the data-fetching of the hurricanes. Wrote all of the most of the manuscript with Paul. Worked out some of the logic for both the flow and the Markov model.
+Performed analysis of historical hurricane data. Contributed to writing and revision of the manuscript. Helped to work out the design and logic for both the MaxFlow and the Markov model.
 
@@
 Designed and implemented the stochastic model.
-Helped Ryan write most of the manuscript.
+Helped Ryan write the manuscript.
 Parsed the county data such as county location and population using the WolframAlpha API.
@@
 \subsection*{Antoine}
-Implemented the flow and Markov models.
+Implemented the MaxFlow and Markov models.
 Created almost all of the graph and network visualizations.
